### 2022-07-07 src/tex/ms.tex
[showyourwork] first commit

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}

% Begin!
\begin{document}

% Title
\title{An open source scientific article}

% Author list
\author{@showyourwork}

% Abstract with filler text
\begin{abstract}
    Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
    Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
    Phasellus eu tellus sit amet tortor gravida placerat. 
    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
    Praesent eget sem vel leo ultrices bibendum. 
    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
    Curabitur auctor semper nulla donec varius orci eget risus. 
    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
    Duis eget orci sit amet orci dignissim rutrum.
\end{abstract}

% Main body with filler text
\section{Introduction}
\label{sec:intro}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
Phasellus eu tellus sit amet tortor gravida placerat. 
Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
Praesent eget sem vel leo ultrices bibendum. 
Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
Curabitur auctor semper nulla donec varius orci eget risus. 
Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
Duis eget orci sit amet orci dignissim rutrum.

Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi. 
Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae. 
Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna. 
Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante. 
Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient. 
Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis. 
Pellentesque cursus luctus mauris \citep{Luger2021}.

\bibliography{bib}

\end{document}

### 2022-07-15 src/scripts/tree.tex
updating

% Adapted from https://tex.stackexchange.com/a/328890
\documentclass[border=5pt]{standalone}
\usepackage{forest}
\usepackage{fontawesome5}
\newcommand\folderOpen{{\color{black!40!white}\faFolderOpen}\hspace{0.4em}}
\newcommand\folderClosed{{\color{black!40!white}\faFolder}\hspace{0.4em}}
\newcommand\file{{\color{black!40!white}\faFile}\hspace{0.7em}}
\begin{document}
\begin{forest}
  for tree={
    font=\ttfamily,
    grow'=0,
    child anchor=west,
    parent anchor=south,
    anchor=west,
    calign=first,
    inner xsep=2pt,
    edge path={
      \noexpand\path [draw, \forestoption{edge}]
      (!u.south west) +(7.5pt,0) |- (.child anchor) \forestoption{edge label};
    },
    before typesetting nodes={
      if n=1
        {insert before={[,phantom]}}
        {}
    },
    fit=band,
    before computing xy={l=15pt},
  }  
[
  \folderOpen repo
  [
    \folderOpen .github
    [
      \folderClosed workflows
    ]
  ]
  [
    \folderOpen src
    [
      \folderClosed data
    ]
    [
      \folderClosed scripts
    ]
    [
      \folderClosed static
    ]
    [
      \folderOpen tex
      [
        \folderClosed figures
      ]
      [
        \folderClosed output
      ]
      [
        \file ms.tex
      ]
    ]
  ]
  [
    \file Snakefile
  ]
  [
    \file environment.yml
  ]
  [
    \file showyourwork.yml
  ]
]
\end{forest}
\end{document}

### 2022-07-15 src/tex/ms.tex
updating

@@
 \documentclass[twocolumn]{aastex631}
+
+% Import showyourwork
 \usepackage{showyourwork}
+
+% Other imports
+\usepackage{listings}
+\usepackage{hyperref}
+\usepackage{enumitem}
+
+% Colors
+\definecolor{fancyblue}{rgb}{0.09,0.35,0.53}
+\colorlet{lsthilite}{fancyblue}
+
+% Code snippet styling
+\lstdefinestyle{bash}{%
+    basicstyle=\ttfamily\footnotesize,
+    numbers=none,
+    breaklines=true,
+    frame=single
+}
+\lstdefinestyle{yaml}{%
+    basicstyle=\ttfamily\footnotesize,
+    numbers=none,
+    breaklines=true,
+    frame=single,
+    morecomment=[l][\color{fancyblue}]{\#}
+}
+\lstdefinestyle{Snakefile}{%
+    basicstyle=\ttfamily\footnotesize,
+    numbers=none,
+    breaklines=true,
+    frame=single,
+    morecomment=[l][\color{fancyblue}]{\#}
+}
+\lstdefinestyle{LaTeX}{%
+    basicstyle=\ttfamily\footnotesize,
+    numbers=none,
+    breaklines=true,
+    frame=single  
+}
+
+% URL styling
+\hypersetup{%
+    linkcolor=fancyblue,
+    citecolor=fancyblue,
+    urlcolor=fancyblue
+}
+
+% List styling
+\setlist[enumerate]{wide=0pt,widest=99,leftmargin=\parindent,labelsep=*}
+\setlist[itemize]{wide=0pt,widest=99,leftmargin=\parindent,labelsep=*}
 
@@
 % Title
-\title{An open source scientific article}
+\title{\showyourwork: a workflow for open source scientific articles}
 
 % Author list
-\author{@showyourwork}
+\author[0000-0002-0296-3826]{Rodrigo Luger}
+\author{Others TBD}
 
@@
 \begin{abstract}
-    Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
-    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
-    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
-    Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
-    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
-    Phasellus eu tellus sit amet tortor gravida placerat. 
-    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
-    Praesent eget sem vel leo ultrices bibendum. 
-    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
-    Curabitur auctor semper nulla donec varius orci eget risus. 
-    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
-    Duis eget orci sit amet orci dignissim rutrum.
+    Abstract coming soon!
 \end{abstract}
@@
 
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
-Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
-Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
-Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
-Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
-Phasellus eu tellus sit amet tortor gravida placerat. 
-Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
-Praesent eget sem vel leo ultrices bibendum. 
-Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
-Curabitur auctor semper nulla donec varius orci eget risus. 
-Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
-Duis eget orci sit amet orci dignissim rutrum.
+This paper introduces \showyourwork, a workflow that enables the creation and distribution of fully reproducible and open source scientific articles. 
+As astronomical software becomes increasingly more complex, and as research results become increasingly more interdependent, it is crucial to ensure the validity and correctness of papers published in the field.
+However, the current peer review system is simply not set up to do this, since checking all of the results in a paper would require the painstaking and methodical review of all of the paper's methods—which usually means scrutinizing all of the code used to generate the figures, tables, and other quantities in the paper.
+In practice, this is virtually impossible for three reasons:
 
-Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi. 
-Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae. 
-Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna. 
-Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante. 
-Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient. 
-Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis. 
-Pellentesque cursus luctus mauris \citep{Luger2021}.
+\begin{enumerate}
+    %
+    \item Modern codebases can be very large and often require deep familiarity with the software to use—not to mention review them.
+    %
+    \item  Writing a paper in astronomy is rarely ever done in a linear, procedural fashion: the codebase is constantly changing, and the state of the code when (say) Figure 1 was produced may be very different from that when (say) Figure 2 was made.
+    Moreover, many results depend on the execution of lengthy pipelines with intermediate steps, each potentially requiring manual tinkering that is not always documented and may be difficult to exactly replicate.
+    %
+    \item The majority of astronomical code is not open source and simply cannot be vetted by third parties. 
+    While there has been a marked increase in the number of open source astronomical tools in recent years (e.g., astropy, exoplanet, emcee, exofast...), most code associated with the generation of the results in individual papers is not open source; readers are often expected to take it on faith that there are no bugs in that code, or that the code works exactly as described in the text, with no pitfalls or missing details.
+    Even when the code is made publicly available, e.g., by being published on \texttt{GitHub}, it is often not documented sufficiently to enable one to execute it and reproduce the paper's results out-of-the-box.
+    And even with proper documentation, the code may require external dependencies, custom virtual environments, or access to closed-source datasets that make it difficult or impossible for a third party to replicate it.
+    %
+\end{enumerate}
+
+\showyourwork was designed to tackle these three issues, making it easy to develop, publish, and distribute truly open and reproducible research papers in astronomy. 
+It exists as a \texttt{GitHub} template repository, which can be cloned at the click of a button to set up a new article. 
+Users then add their LaTeX manuscript, bibliography, scripts used in the generation of the paper's figures, an anaconda environment specification, and instructions on how to download any external datasets required by the figures.
+Every time the user pushes a new commit to \texttt{GitHub}, the article is automatically built on the cloud using \texttt{GitHub Actions} and the resulting PDF is pushed to a separate branch of the repository.
+The build step—which sets up the conda environment, generates all figures from scratch (with intelligent caching), and compiles the PDF—acts as a unit test for the paper. 
+If it passes, the paper is (by definition) reproducible.
+
+The workflow works out of the box for simple projects, in which each figure is generated by running a given \texttt{Python} script. 
+But it also works for more complicated pipelines, such as projects that depend on many intermediate steps or those that require running expensive simulations on clusters. 
+The workflow interfaces directly with \texttt{Zenodo}, allowing users to automatically upload the results of simulations so that expensive build steps can be bypassed on the cloud. 
+In fact, most of the stuff under the hood is there to make the workflow as flexible and customizable as possible; see the documentation for a list of examples of custom workflows.
+
+Papers that use this workflow can be reproduced by cloning the repository and running \texttt{make}. 
+Furthermore, these papers include clickable icons next to each of their figures linking to (1) the exact version of the script used to generate them and (2) the exact version(s) of the \texttt{Zenodo}-hosted dataset(s) used in their creation.
+
+\section{Examples}
+\label{sec:examples}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/eccentricity.pdf}
+        \caption{
+            The effect of binary eccentricity on the detectability of a \emph{LISA} gravitational wave source; reproduced from Figure 3 in \citet{Wagg2022}. 
+            This figure was automatically generated from the script \texttt{src/figures/eccentricity.py}.
+        }
+        \label{fig:eccentricity}
+        \script{eccentricity.py}
+    \end{centering}
+\end{figure}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/luhman16b.pdf}
+        \caption{
+            16 \emph{CRIRES} spectra of WISE 1049-5319B spanning a full rotation period of the brown dwarf; adapted from Figure 14 in \citet{Luger2021} and based on data from \citet{Crossfield2014}.
+            This figure was automatically generated from the script \texttt{src/figures/luhman16b.py} and a dataset downloaded from \texttt{Zenodo}.
+        }
+        \label{fig:luhman16b}
+        \script{luhman16b.py}
+    \end{centering}
+\end{figure}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/two_moons.pdf}
+        \caption{
+            Hello!
+        }
+        \label{fig:two_moons}
+        \script{two_moons.py}
+    \end{centering}
+\end{figure}
+
+\section{Prerequisites}
+\label{sec:prereq}
+Conda. Linux/UNIX/Mac. GitHub account.
+
+\section{Starting a project}
+\label{sec:start}
+%
+Coming soon.
+
+\section{Reproducing a project}
+\label{sec:reproduce}
+%
+Any project based on \showyourwork can be reproduced by cloning its \texttt{GitHub} repository and running \texttt{showyourwork}:\\
+
+\noindent\begin{minipage}{\linewidth}
+\begin{lstlisting}[
+    style=bash,
+    otherkeywords={user,repo},
+    emph={user,repo},
+    emphstyle={\color{lsthilite}}
+]
+git clone https://github.com/user/repo
+cd repo
+showyourwork
+\end{lstlisting}
+\end{minipage}
+
+\section{Local builds}
+\label{sec:local-builds}
+%
+Coming soon.
+
+\section{Remote builds}
+\label{sec:remote-builds}
+%
+Coming soon.
+
+\section{Repository structure}
+\label{sec:struct}
+%
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=0.5\linewidth]{figures/tree.pdf}
+        \caption{
+            The basic repository structure for an open source scientific article.
+            See text for details.
+        }
+        \label{fig:tree}
+        \script{tree.tex}
+    \end{centering}
+\end{figure}
+%
+Figure~\ref{fig:tree} shows the basic directory structure for a repository instantiated from \texttt{showyourwork-template}. 
+The main components are:
+\begin{itemize}
+    \item \texttt{.github/workflows}: Contains configuration files for the \texttt{GitHub Actions} workflows, with instructions on how to set up the virtual environment, checkout the repository, and invoke the \texttt{showyourwork-action} to build and publish the article PDF.
+    \item \texttt{src/data}: Contains programmatically generated (or downloaded) datasets and dependencies that are not tracked by \texttt{git}.
+    \item \texttt{src/scripts}: Contains all of the scripts and auxiliary code needed to generate the article figures.
+    \item \texttt{src/static}: Contains miscellaneous files (usually figures) that are tracked by \texttt{git}.
+    These may include photographs, flowcharts, or other figures that cannot be programmatically generated.
+    \item \texttt{src/tex}: Contains the article manuscript and other auxiliary \texttt{TeX} files, such as the bibliography.
+    \item \texttt{Snakefile}: A file containing the rules for the \texttt{Snakemake} workflow; see \S\ref{sec:Snakefile}
+    By default, it simply imports all of the rules defined in \texttt{showyourwork/workflow/Snakefile}, but users can edit this file to add new rules or customize existing rules.
+    \item \texttt{environment.yml}: The \texttt{conda} environment file specifying all of the direct software dependencies of the workflow; see \S\ref{sec:environmentyml}
+    \item \texttt{showyourwork.yml}: The main configuration file for the workflow, where users can specify figure and dataset dependencies, instructions for downloading datasets from \texttt{Zenodo}, etc.; see \S\ref{sec:showyourworkyml}
+\end{itemize}
+
+\section{Automatic figure generation}
+\label{sec:auto-fig}
+%
+The workflow automatically determines the relationship between a figure (e.g., a \texttt{*.pdf} image) and the script that generated it (e.g., a \texttt{*.py} file) via inspection of the \texttt{figure} environment in the \texttt{TeX} file.
+Specifically, it inspects the \texttt{{\textbackslash}includegraphics} and \texttt{{\textbackslash}label} commands to infer the name of the figure and the script that generated it, respectively.
+Consider the following snippet, used to generate Figure~\ref{fig:eccentricity}:\\
+
+\noindent\begin{minipage}{\linewidth}
+\begin{lstlisting}[
+    style=LaTeX,
+    otherkeywords={figures/eccentricity.pdf,fig:eccentricity},
+    emph={figures/eccentricity.pdf,fig:eccentricity},
+    emphstyle={\color{lsthilite}}
+]
+\begin{figure}
+  \begin{centering}
+    \includegraphics{figures/eccentricity.pdf}
+    \caption{...}
+    \label{fig:eccentricity}
+  \end{centering}
+\end{figure}
+\end{lstlisting}
+\end{minipage}
+
+\noindent The convention in \showyourwork is to infer the parent script for a figure referenced in an \texttt{includegraphics} call (in this case, {\color{lsthilite}\texttt{figures/eccentricity.pdf}}) from the figure \texttt{label}.
+Specifically, if a label starts with {\color{lsthilite}\texttt{fig:}}, the remainder of the label (e.g., {\color{lsthilite}\texttt{eccentricity}}) is interpreted as the name of a script in the \texttt{figures/} directory which should be executed to produce that figure.
+By default, figure scripts are expected to be \texttt{Python} scripts, so in this case the workflow will attempt to run\\
+
+\noindent\begin{minipage}{\linewidth}
+\begin{lstlisting}[
+    style=bash
+]
+python eccentricity.py
+\end{lstlisting}
+\end{minipage}
+
+\noindent from within the \texttt{figures/} directory to generate \texttt{eccentricity.pdf}.
+
+This behavior may be customized in several ways. 
+For instance, the figure script need not be a \texttt{Python} script; see \S\ref{sec:other-lang} for information on how to include scripts in any language.
+Another common scenario involves a script that generates multiple figures.
+These can all be included (using \texttt{{\textbackslash}includegraphics}) in the same figure environment with a single shared label (denoting the name of the script), or in multiple different figure environments by appending an arbitrary suffix to each figure label to make them all unique (i.e., \texttt{fig:eccentricity:one}, \texttt{fig:eccentricity:two}, etc.)
+And finally, this behavior may be overridden entirely by either placing the figure in the \texttt{src/static} directory (and committing it directly to the \texttt{GitHub} repository) or by supplying a label that instead begins with \texttt{fig*:}, which instructs the workflow to not attempt to programmatically generate the figure.
+In the latter case, a custom rule must be provided in the \texttt{Snakefile} to generate it (see, e.g., Figure~\ref{fig*:v1298tau}).
+
+\section{Support for other languages}
+\label{sec:other-lang}
+%
+Scripts in languages other than \texttt{Python} are supported via the inclusion of entries under the \texttt{scripts} key in the \texttt{showyourwork.yml} config file. 
+Consider Figure~\ref{fig:tree}, which was generated from the \texttt{TeX} file \texttt{figures/tree.tex}, which contains a \texttt{TikZ} picture. 
+In the main manuscript, we include the figure in the usual way, i.e.,\\
+
+\noindent\begin{minipage}{\linewidth}
+\begin{lstlisting}[
+    style=LaTeX,
+    otherkeywords={figures/eccentricity.pdf,fig:eccentricity},
+    emph={figures/eccentricity.pdf,fig:eccentricity},
+    emphstyle={\color{lsthilite}}
+]
+\begin{figure}
+  \begin{centering}
+    \includegraphics{figures/tree.pdf}
+    \caption{...}
+    \label{fig:tree}
+  \end{centering}
+\end{figure}
+\end{lstlisting}
+\end{minipage}
+
+\noindent By default, as we saw in \S\ref{sec:auto-fig}, this instructs the workflow to execute a file called \texttt{figures/tree.py} to generate the corresponding figure. 
+However, in the present case, that file does not exist; instead, we have a file called \texttt{figures/tree.tex}, which we would like to compile into a \texttt{PDF} using te \texttt{tectonic} engine.
+We can instruct the workflow to do this by specifying the following in \texttt{showyourwork.yml}:\\
+
+\noindent\begin{minipage}{\linewidth}
+\begin{lstlisting}[
+    style=yaml,
+    otherkeywords={script.path,script.name},
+    emph={script.path,script.name},
+    emphstyle={\color{lsthilite}}
+]
+scripts:
+  tex:
+    cd {script.path} && tectonic {script.name}
+\end{lstlisting}
+\end{minipage}
+
+\noindent Each entry under the \texttt{scripts} key should be a file extension, and under each one, a string containing a shell command that instructs the workflow how to execute a given {\color{lsthilite}\texttt{script}} to produce a given {\color{lsthilite}\texttt{output}}.
+For convenience, the following placeholders are recognized and expand as follows at runtime:
+%
+\begin{itemize}
+\item \texttt{\{script\}}: The full path to the input script.
+\item \texttt{\{script.path\}}: The full path to the directory containing the input script.
+\item \texttt{\{script.name\}}: The name of the input script (without the path).
+\item \texttt{\{output\}}: The full path to the output file.
+\item \texttt{\{output.path\}}: The full path to the directory containing the output file.
+\item \texttt{\{output.name\}}: The name of the output file (without the path).
+\end{itemize}
+%
+If additional customization is needed, such as the need to provide command-line arguments that are specific to individual figures, users should instead provide custom rules in the \texttt{Snakefile} (\S\ref{sec:arbitrary-rules}).
+
+\section{Arbitrary rules}
+\label{sec:arbitrary-rules}
+%
+Coming soon.
+
+\section{Zenodo interface}
+\label{sec:zenodo}
+%
+Coming soon.
+
+\section{This paper}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/dag.pdf}
+        \caption{
+            A directed acyclic graph (DAG) showing the build process for each of the (other) figures in this article. 
+        }
+        \label{fig:dag}
+    \end{centering}
+\end{figure}
 

### 2022-07-15 src/scripts/eccentricity.py

@@ -1,0 +1,151 @@
+"""
+This is the script that generates Figure 3 in Wagg et al. (2021).
+
+Original version:
+
+https://github.com/TeamLEGWORK/LEGWORK-paper/blob/d0afa5/src/figures/role_eccentricity.py
+
+Original caption:
+
+An illustration of the effect of eccentricity on the detectability 
+of a LISA source. The three sets of points are coloured by their 
+eccentricity and each individual point corresponds to a harmonic 
+frequency, where its height above the curve gives its SNR. We 
+annotate each set of points with its total SNR and overlay the 
+LISA sensitivity curve. The dotted vertical lines indicate the 
+frequency at which the ma- jority of the gravitational wave signal 
+is concentrated.
+
+"""
+
+import legwork as lw
+import numpy as np
+import astropy.units as u
+import matplotlib.pyplot as plt
+from astropy.visualization import quantity_support
+import paths
+
+quantity_support()
+
+plt.rc("font", family="serif")
+plt.rcParams["text.usetex"] = False
+fs = 24
+
+# update various fontsizes to match
+params = {
+    "figure.figsize": (12, 8),
+    "legend.fontsize": fs,
+    "axes.labelsize": fs,
+    "xtick.labelsize": 0.9 * fs,
+    "ytick.labelsize": 0.9 * fs,
+    "axes.linewidth": 1.1,
+    "xtick.major.size": 7,
+    "xtick.minor.size": 4,
+    "ytick.major.size": 7,
+    "ytick.minor.size": 4,
+}
+plt.rcParams.update(params)
+
+# set eccentricities
+ecc = np.array([1e-6, 0.6, 0.9])
+n_binaries = len(ecc)
+
+# use constant values for mass, f_orb and distance
+m_1 = np.repeat(0.6, n_binaries) * u.Msun
+m_2 = np.repeat(0.6, n_binaries) * u.Msun
+f_orb = np.repeat(1.5e-3, n_binaries) * u.Hz
+dist = np.repeat(15, n_binaries) * u.kpc
+
+# get the SNR in each harmonic
+snr2_n = lw.snr.snr_ecc_evolving(
+    m_1=m_1,
+    m_2=m_2,
+    f_orb_i=f_orb,
+    ecc=ecc,
+    dist=dist,
+    harmonics_required=100,
+    t_obs=4 * u.yr,
[…]

### 2022-07-15 src/scripts/luhman16b.py

@@ -1,0 +1,88 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import pickle
+import paths
+
+
+# Load the dataset
+with open(paths.data / "luhman16b.pickle", "rb") as f:
+    data = pickle.load(f, encoding="latin1")
+
+# Timestamps (from Ian Crossfield)
+t = np.array(
+    [
+        0.0,
+        0.384384,
+        0.76825872,
+        1.15339656,
+        1.5380364,
+        1.92291888,
+        2.30729232,
+        2.69268336,
+        3.07654752,
+        3.46219464,
+        3.8473428,
+        4.23171624,
+        4.61583456,
+        4.99971048,
+    ]
+)
+
+# Use the first epoch's wavelength array
+lams = data["chiplams"][0]
+
+# Interpolate onto that array
+observed = np.empty((14, 4, 1024))
+template = np.empty((14, 4, 1024))
+broadened = np.empty((14, 4, 1024))
+for k in range(14):
+    for c in range(4):
+        observed[k][c] = np.interp(
+            lams[c],
+            data["chiplams"][k][c],
+            data["obs1"][k][c] / data["chipcors"][k][c],
+        )
+        template[k][c] = np.interp(
+            lams[c],
+            data["chiplams"][k][c],
+            data["chipmodnobroad"][k][c] / data["chipcors"][k][c],
+        )
+        broadened[k][c] = np.interp(
+            lams[c],
+            data["chiplams"][k][c],
+            data["chipmods"][k][c] / data["chipcors"][k][c],
+        )
+
+# Get the final data arrays
+wav = data["chiplams"][:, 2]
+flux = data["obs1"][:, 2] / data["chipcors"][:, 2]
+model = data["chipmods"][:, 2] / data["chipcors"][:, 2]
+
+# Plot the spectra
+fig, ax = plt.subplots(1, figsize=(8, 5))
+fig.subplots_adjust(wspace=0.1)
+for k in range(14):
+    ax.plot(wav[k], 0.65 * k + flux[k], "k.", ms=2, alpha=0.5, zorder=-1)
+    ax.plot(wav[k], 0.65 * k + model[k], "C1-", lw=1)
+
+# Appearance hacks
+ax.spines["left"].set_visible(False)
[…]

### 2022-07-15 src/scripts/train_two_moons_flow.py

@@ -1,0 +1,14 @@
+"""Train the flow for the two moons example."""
+from pzflow import Flow
+from pzflow.examples import get_twomoons_data
+import paths
+
+# load the two moons example data
+data = get_twomoons_data()
+
+# create and train a flow to model the two moons data
+flow = Flow(data.columns)
+_ = flow.train(data)
+
+# save the trained flow
+flow.save(paths.data / "two_moons_flow.pzflow.pkl")

### 2022-07-15 src/scripts/two_moons.py

@@ -1,0 +1,124 @@
+"""Create the two moons example figure."""
+import matplotlib.pyplot as plt
+import numpy as np
+from matplotlib.gridspec import GridSpec
+from pzflow import Flow
+from pzflow.examples import get_twomoons_data
+import paths
+
+# load the two moons example data
+data = get_twomoons_data()
+
+# load the trained flow
+flow = Flow(file=paths.data / "two_moons_flow.pzflow.pkl")
+
+# calculate the latent variables for a subset of the data
+samples = data[:5_000].to_numpy()
+latents = flow._forward(
+    flow._params[1], samples, conditions=np.zeros((samples.shape[0], 1))
+)[0]
+
+
+# set the colors of the samples
+def thread(x: np.ndarray) -> np.ndarray:
+    """Calculate function that threads between the two moons."""
+    return 0.5 * np.sin(-3 * (x - 0.5)) + 0.25
+
+
+colors = []
+for row in samples:
+    # upper moon
+    if thread(row[0]) < row[1]:
+        # left half
+        if row[0] < 0:
+            colors.append("C0")
+        # right half
+        else:
+            colors.append("C1")
+
+    # lower moon
+    else:
+        # left half
+        if row[0] > 1:
+            colors.append("C2")
+        # right half
+        else:
+            colors.append("C3")
+
+
+# create the figure
+fig = plt.figure(figsize=(6, 2.6), constrained_layout=True)
+gs = GridSpec(1, 5, figure=fig)
+
+# make the scatter plots
+scatter_settings = {
+    "c": colors,
+    "marker": ".",
+    "s": 3,
+    "rasterized": True,
+}
+
+# scatter plot of data (left panel)
+ax1 = fig.add_subplot(gs[:2])
+ax1.scatter(samples[:, 0], samples[:, 1], **scatter_settings)
+ax1.set(
+    title="Data Space",
+    xlim=(-1.5, 2.5),
+    ylim=(-1.5, 2),
+    xticks=[],
+    yticks=[],
+    aspect=4 / 3.5,
+)
+
+# scatter plot of latents (right panel)
+ax2 = fig.add_subplot(gs[3:])
+ax2.scatter(latents[:, 0], latents[:, 1], **scatter_settings)
+ax2.set(
+    title="Latent Space",
+    xlim=(-5.5, 5.5),
[…]

### 2022-07-15 src/tex/ms.tex
update syw

--- 2022-07-07 src/tex/ms.tex
@@
 % Define document class
-\documentclass[twocolumn]{aastex631}
+\documentclass[modern]{aastex631}
+
+% Import showyourwork
 \usepackage{showyourwork}
+
+% Other imports
+\usepackage{listings}
+\usepackage{hyperref}
+\usepackage{enumitem}
+
+% Colors
+\definecolor{fancyblue}{rgb}{0.09,0.35,0.53}
+\colorlet{lsthilite}{fancyblue}
+
+% Code snippet styling
+\lstdefinestyle{bash}{%
+    basicstyle=\ttfamily\footnotesize,
+    numbers=none,
+    breaklines=true,
+    frame=single
+}
+\lstdefinestyle{yaml}{%
+    basicstyle=\ttfamily\footnotesize,
+    numbers=none,
+    breaklines=true,
+    frame=single,
+    morecomment=[l][\color{fancyblue}]{\#}
+}
+\lstdefinestyle{Snakefile}{%
+    basicstyle=\ttfamily\footnotesize,
+    numbers=none,
+    breaklines=true,
+    frame=single,
+    morecomment=[l][\color{fancyblue}]{\#}
+}
+\lstdefinestyle{LaTeX}{%
+    basicstyle=\ttfamily\footnotesize,
+    numbers=none,
+    breaklines=true,
+    frame=single  
+}
+
+% URL styling
+\hypersetup{%
+    linkcolor=fancyblue,
+    citecolor=fancyblue,
+    urlcolor=fancyblue
+}
+
+% List styling
+\setlist[enumerate]{wide=0pt,widest=99,leftmargin=\parindent,labelsep=*}
+\setlist[itemize]{wide=0pt,widest=99,leftmargin=\parindent,labelsep=*}
 
@@
 \begin{abstract}
-    Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
-    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
-    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
-    Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
-    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
-    Phasellus eu tellus sit amet tortor gravida placerat. 
-    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
-    Praesent eget sem vel leo ultrices bibendum. 
-    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
-    Curabitur auctor semper nulla donec varius orci eget risus. 
-    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
-    Duis eget orci sit amet orci dignissim rutrum.
+    This paper introduces \texttt{showyourwork!}, a workflow that enables the creation and distribution of fully reproducible and open source scientific articles.
 \end{abstract}
@@
 \label{sec:intro}
+As astronomical research software becomes increasingly more complex, and as research results become increasingly more interdependent, it becomes ever more challenging to ensure the validity and correctness of results published in the literature.
+Unfortunately, the current peer review system in astronomy is simply not set up to do this.
+Checking all of the results in a paper would require the painstaking and methodical review of all of the paper's methods---which usually means scrutinizing all of the code used to generate the figures, tables, and other quantities in the paper.
+In practice, this is virtually impossible for three reasons:
 
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
-Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
-Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
-Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
-Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
-Phasellus eu tellus sit amet tortor gravida placerat. 
-Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
-Praesent eget sem vel leo ultrices bibendum. 
-Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
-Curabitur auctor semper nulla donec varius orci eget risus. 
-Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
-Duis eget orci sit amet orci dignissim rutrum.
+\begin{enumerate}
+    %
+    \item Modern codebases can be very large and often require deep familiarity with the software to use---not to mention review them.
+Volunteer referees rarely have the time to invest in learning new software in order to provide a comprehensive review.
+    %
+    \item  Writing a paper in astronomy is rarely ever done in a linear, procedural fashion: the codebase is constantly changing, and the state of the code when (say) Figure 1 was produced may be very different from that when (say) Figure 2 was made.
+    Moreover, many results depend on the execution of lengthy pipelines with intermediate steps, each potentially requiring manual tinkering that is not always documented and may be difficult to replicate exactly.
+    %
+    \item The majority of astronomical code is not open source and simply cannot be vetted by third parties. 
+    While there has been a marked increase in the number of open source astronomical tools in recent years (e.g., \texttt{astropy}, \texttt{exoplanet}, \texttt{emcee}, \texttt{exofast}...), most code associated with the generation of the results in individual papers is not open source; readers are often expected to take it on faith that there are no bugs in that code, or that the code works exactly as described in the text, with no pitfalls or missing details.
+    Even when the code is made publicly available, e.g., by being published on \texttt{GitHub}, it is often not documented sufficiently to enable one to execute it and reproduce the paper's results out-of-the-box.
+    And even with proper documentation, the code may require external dependencies, custom virtual environments, or access to closed-source datasets that make it difficult or impossible for a third party to replicate it.
+    %
+\end{enumerate}
 
-Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi. 
-Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae. 
-Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna. 
-Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante. 
-Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient. 
-Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis. 
-Pellentesque cursus luctus mauris \citep{Luger2021}.
+\texttt{showyourwork!} was designed to tackle these three issues, making it easy to develop, publish, and distribute truly open and reproducible research papers in astronomy and other scientific disciplines.
+At its core, it is a command-line tool that builds papers from a set of instructions contained in a \texttt{GitHub} repository and organized into \texttt{TeX} files, figure scripts, pipeline files, and configuration/specifications files.
+Every time the user pushes a new commit to \texttt{GitHub}, the article is automatically built on the cloud using \texttt{GitHub Actions} and the resulting PDF is pushed to a separate branch of the repository.
+The build step---which sets up the conda environment, generates all figures from scratch (with intelligent caching), and compiles the PDF---acts as a unit test for the paper. 
+If it passes, the paper is (by definition) reproducible.
+
+\texttt{showyourwork!} works out of the box for simple projects, in which each figure is generated by running a given script. 
+But it also works for more complicated pipelines, such as projects that depend on many intermediate steps or those that require running expensive simulations on clusters. 
+The workflow interfaces directly with \texttt{Zenodo}, allowing users to automatically upload the results of simulations so that expensive build steps can be bypassed on the cloud. 
+In fact, most of the features under the hood are there to make the workflow as flexible and customizable as possible.
+
+Papers that use \texttt{showyourwork!} can be reproduced by cloning the associated repository and running \texttt{showyourwork}. 
+Such papers (like this one!) include clickable icons next to each of their figures linking to (1) the exact version of the script on \texttt{GitHub} used to generate them and (2) the exact version(s) of the \texttt{Zenodo}-hosted dataset(s) used in their creation.
+
+\section{Using \showyourwork}
+\label{sec:usage}
+
+\subsection{Prerequisites}
+\label{sec:usage:prereq}
+\texttt{showyourwork!} requires the \texttt{conda} package manager\footnote{\url{https://www.anaconda.com/products/distribution}} and is currently tested only on Unix-like operating systems (such as Linux, Ubuntu, or MacOS).
+Users must also have access to a \texttt{GitHub} account; other \texttt{git} platforms are not currently supported.
+Note that users do \emph{not} need a local installation of a \texttt{TeX} distribution, as \texttt{showyourwork!} uses the \texttt{conda}-managed \texttt{tectonic} package to compile articles.
+
+\subsection{Installation}
+\label{sec:usage:install}
+\texttt{showyourwork!} can be installed with the \texttt{Python} package manager \texttt{pip}:\\
+
+\noindent\begin{minipage}{\linewidth}
+\begin{lstlisting}[
+    style=bash
+]
+python -m pip install -U showyourwork
+\end{lstlisting}
+\end{minipage}
+
+\noindent (recommended) or from source on \texttt{GitHub}:\\
+
+\noindent\begin{minipage}{\linewidth}
+\begin{lstlisting}[
+    style=bash
+]
+git clone https://github.com/showyourwork/showyourwork
+cd showyourwork
+python -m pip install .
+\end{lstlisting}
+\end{minipage}
+
+\subsection{Reproducing an article}
+\label{sec:usage:reproduce}
+Any project based on \texttt{showyourwork!} can be reproduced by cloning its \texttt{GitHub} repository and running \texttt{showyourwork}. For example, to reproduce this paper, run:\\
+
+\noindent\begin{minipage}{\linewidth}
+\begin{lstlisting}[
+    style=bash,
+    otherkeywords={user,repo},
+    emph={user,repo},
+    emphstyle={\color{lsthilite}}
+]
+git clone https://github.com/showyourwork/showyourwork-paper
+cd showyourwork-paper
+showyourwork
+\end{lstlisting}
+\end{minipage}
+
+\noindent This will set up a custom \texttt{conda} environment for the workflow, download the required datasets from \texttt{Zenodo}, build all of the figures, and generate a PDF identical to this one.
+
+\subsection{Creating a new article}
+\label{sec:usage:new}
+Coming soon.
+
+\section{Repository structure}
+\label{sec:struct}
+%
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=0.25\linewidth]{figures/tree.pdf}
+        \caption{
+            The basic repository structure for an open source scientific article built with \texttt{showyourwork!}.
+            This figure was automatically generated from the \texttt{TikZ} code in \texttt{src/scripts/tree.tex} by specifying a custom command in \texttt{showyourwork.yml}.
+        }
+        \label{fig:tree}
+        \script{tree.tex}
+    \end{centering}
+\end{figure}
+%
+Figure~\ref{fig:tree} shows the basic directory structure for a repository instantiated from \texttt{showyourwork-template}. 
+The main components are:
+\begin{itemize}
+    \item \texttt{.github/workflows}: Contains configuration files for the \texttt{GitHub Actions} workflows, with instructions on how to set up the virtual environment, checkout the repository, and invoke the \texttt{showyourwork-action} to build and publish the article PDF.
+    \item \texttt{src/data}: Contains programmatically generated (or downloaded) datasets and dependencies that are not tracked by \texttt{git}.
+    \item \texttt{src/scripts}: Contains all of the scripts and auxiliary code needed to generate the article figures.
+    \item \texttt{src/static}: Contains miscellaneous files (usually figures) that are tracked by \texttt{git}.
+    These may include photographs, flowcharts, or other figures that cannot be programmatically generated.
+    \item \texttt{src/tex}: Contains the article manuscript and other auxiliary \texttt{TeX} files, such as the bibliography.
+    \item \texttt{Snakefile}: A file containing the rules for the \texttt{Snakemake} workflow.
+    By default, it simply imports all of the rules defined in \texttt{showyourwork/workflow/Snakefile}, but users can edit this file to add new rules or customize existing rules.
+    \item \texttt{environment.yml}: The \texttt{conda} environment file specifying all of the direct software dependencies of the workflow.
+    \item \texttt{showyourwork.yml}: The main configuration file for the workflow, where users can specify figure and dataset dependencies, instructions for downloading datasets from \texttt{Zenodo}.
+\end{itemize}
+
+\section{Examples}
+\label{sec:examples}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/eccentricity.pdf}
+        \caption{
+            The effect of binary eccentricity on the detectability of a \emph{LISA} gravitational wave source; reproduced from Figure 3 in \citet{Wagg2022}. 
+            This figure was automatically generated from the script \texttt{src/scripts/eccentricity.py}.
+        }
+        \label{fig:eccentricity}
+        \script{eccentricity.py}
+    \end{centering}
+\end{figure}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/luhman16b.pdf}
+        \caption{
+            16 \emph{CRIRES} spectra of WISE 1049-5319B spanning a full rotation period of the brown dwarf; adapted from Figure 14 in \citet{Luger2021} and based on data from \citet{Crossfield2014}.
+            This figure was automatically generated from the script \texttt{src/scripts/luhman16b.py} and a dataset downloaded from \texttt{Zenodo}.
+        }
+        \label{fig:luhman16b}
+        \script{luhman16b.py}
+    \end{centering}
+\end{figure}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/two_moons.pdf}
+        \caption{
+            A normalizing flow demonstrated on the two moons data set from \texttt{scikit-learn};
+            reproduced from Figure 1 in \citet{Crenshaw2022}.
+            This figure was automatically generated from the script \texttt{src/scripts/two\_moons.py}
+            and an intermediate dataset that was automatically cached on \texttt{Zenodo}.
+        }
+        \label{fig:two_moons}
+        \script{two_moons.py}
+    \end{centering}
+\end{figure}
+
+\section{Integration with Zenodo}
+\label{sec:zenodo}
+%
+Coming soon.
+
+\section{This paper}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/dag.pdf}
+        \caption{
+            A directed acyclic graph (DAG) showing the complete list of dependencies for the article. 
+            Scripts are shown in green, \texttt{Zenodo} deposits in blue, datasets in purple, and \texttt{TeX} files in red.
+            This figure is located in the \texttt{src/static} directory and, unlike the other figures in this article, is version controlled by \texttt{git}.
+The \texttt{src/static} directory is reserved for figures that are not programmatically generated and simply get copied over to the output directory at compile time.
+        }
+        \label{fig:dag}
+    \end{centering}
+\end{figure}
 

### 2022-07-19 src/scripts/tree.tex
updates

@@
 [
-  \folderOpen repo
+  \folderOpen
   [
@@
     [
-      \folderClosed workflows
+      \folderClosed workflows {\sffamily \color{gray} --- Configuration files for GitHub Actions workflows}
     ]
@@
     [
-      \folderClosed data
+      \folderClosed data {\sffamily \color{gray} --- Programmatically generated or downloaded datasets}
     ]
     [
-      \folderClosed scripts
+      \folderClosed scripts {\sffamily \color{gray} --- Scripts and auxiliary code for generating figures}
     ]
     [
-      \folderClosed static
+      \folderClosed static {\sffamily \color{gray} --- Version-controlled figures (photographs, charts, etc.)}
     ]
@@
       [
-        \folderClosed figures
+        \folderClosed figures {\sffamily \color{gray} --- Programmatically generated figures}
       ]
       [
-        \folderClosed output
+        \folderClosed output {\sffamily \color{gray} --- Other programmatically generated output}
       ]
       [
-        \file ms.tex
+        \file ms.tex {\sffamily \color{gray} --- Main article manuscript}
       ]
@@
   [
-    \file Snakefile
+    \file Snakefile {\sffamily \color{gray} --- Custom \texttt{snakemake} rules}
   ]
   [
-    \file environment.yml
+    \file environment.yml {\sffamily \color{gray} --- \texttt{conda} environment specifications}
   ]
   [
-    \file showyourwork.yml
+    \file showyourwork.yml {\sffamily \color{gray} --- Workflow configuration}
   ]

### 2022-07-19 src/tex/ms.tex
updates

@@
 % Other imports
+\usepackage{etoolbox}
 \usepackage{listings}
@@
 \usepackage{enumitem}
+\usepackage{tikz}
 
@@
 \definecolor{fancyblue}{rgb}{0.09,0.35,0.53}
+\definecolor{codebkg}{rgb}{0.89,0.89,0.89}
 \colorlet{lsthilite}{fancyblue}
@@
 % Code snippet styling
+\usepackage[%
+    framemethod=tikz,
+    skipbelow=\topskip,
+    skipabove=\topskip
+]{mdframed}
+\mdfsetup{%
+    leftmargin=0pt,
+    rightmargin=0pt,
+    backgroundcolor=codebkg,
+    middlelinecolor=black,
+    roundcorner=5
+}
+\BeforeBeginEnvironment{lstlisting}{\begin{mdframed}\vspace{-0.5em}}
+\AfterEndEnvironment{lstlisting}{\vspace{-0.5em}\end{mdframed}}
+\lstdefinestyle{base}{%
+    basicstyle=\footnotesize\ttfamily,
+    breaklines=true,
+    captionpos=b
+}
 \lstdefinestyle{bash}{%
-    basicstyle=\ttfamily\footnotesize,
-    numbers=none,
-    breaklines=true,
-    frame=single
+    style=base
 }
@@
 
-% List styling
-\setlist[enumerate]{wide=0pt,widest=99,leftmargin=\parindent,labelsep=*}
-\setlist[itemize]{wide=0pt,widest=99,leftmargin=\parindent,labelsep=*}
+% Other stuff
+\newcommand\syw{\texttt{showyourwork}\xspace}
+\newcommand\fileurl[1]{https://github.com/showyourwork/showyourwork-paper/blob/\GitHubSHA/#1}
 
@@
 \begin{abstract}
-    This paper introduces \texttt{showyourwork!}, a workflow that enables the creation and distribution of fully reproducible and open source scientific articles.
+    This paper introduces \syw, a workflow that enables the creation and distribution of fully reproducible and open source scientific articles.
 \end{abstract}
@@
 
-\texttt{showyourwork!} was designed to tackle these three issues, making it easy to develop, publish, and distribute truly open and reproducible research papers in astronomy and other scientific disciplines.
+\syw was designed to tackle these three issues, making it easy to develop, publish, and distribute truly open and reproducible research papers in astronomy and other scientific disciplines. 
 At its core, it is a command-line tool that builds papers from a set of instructions contained in a \texttt{GitHub} repository and organized into \texttt{TeX} files, figure scripts, pipeline files, and configuration/specifications files.
@@
 
-\texttt{showyourwork!} works out of the box for simple projects, in which each figure is generated by running a given script. 
+\syw works out of the box for simple projects, in which each figure is generated by running a given script. 
 But it also works for more complicated pipelines, such as projects that depend on many intermediate steps or those that require running expensive simulations on clusters. 
@@
 
-Papers that use \texttt{showyourwork!} can be reproduced by cloning the associated repository and running \texttt{showyourwork}. 
+Papers that use \syw can be reproduced by cloning the associated repository and running \syw. 
 Such papers (like this one!) include clickable icons next to each of their figures linking to (1) the exact version of the script on \texttt{GitHub} used to generate them and (2) the exact version(s) of the \texttt{Zenodo}-hosted dataset(s) used in their creation.
 
-\section{Using \showyourwork}
+\section{Using {\protect\syw}}
 \label{sec:usage}
+In this section we provide basic, high-level instructions on how to install and use \syw.
+These instructions are for version \texttt{0.3.0} of the code, the current version at the time of writing (July 2022) and are subject to change in future releases.
+For more details, including custom commands, settings, examples, and troubleshooting tops, please refer to the documentation for the specific version of \syw at \url{https://show-your.work}.
 
@@
 \label{sec:usage:prereq}
-\texttt{showyourwork!} requires the \texttt{conda} package manager\footnote{\url{https://www.anaconda.com/products/distribution}} and is currently tested only on Unix-like operating systems (such as Linux, Ubuntu, or MacOS).
+\syw requires the \texttt{conda} package manager\footnote{\url{https://www.anaconda.com/products/distribution}} and is currently tested only on Unix-like operating systems (such as Linux, Ubuntu, or MacOS).
 Users must also have access to a \texttt{GitHub} account; other \texttt{git} platforms are not currently supported.
-Note that users do \emph{not} need a local installation of a \texttt{TeX} distribution, as \texttt{showyourwork!} uses the \texttt{conda}-managed \texttt{tectonic} package to compile articles.
+Note that users do \emph{not} need a local installation of a \texttt{TeX} distribution, as \syw uses the \texttt{conda}-managed \texttt{tectonic} package to compile articles.
 
@@
 \label{sec:usage:install}
-\texttt{showyourwork!} can be installed with the \texttt{Python} package manager \texttt{pip}:\\
+\syw can be installed with the \texttt{Python} package manager \texttt{pip}:\\
 
@@
 \label{sec:usage:reproduce}
-Any project based on \texttt{showyourwork!} can be reproduced by cloning its \texttt{GitHub} repository and running \texttt{showyourwork}. For example, to reproduce this paper, run:\\
+Any project based on \syw can be reproduced by cloning its \texttt{GitHub} repository and running \syw. For example, to reproduce this paper, run:\\
 
@@
 \begin{lstlisting}[
-    style=bash,
-    otherkeywords={user,repo},
-    emph={user,repo},
-    emphstyle={\color{lsthilite}}
+    style=bash
 ]
@@
 \label{sec:usage:new}
-Coming soon.
+New projects may be created by running\\
 
-\section{Repository structure}
-\label{sec:struct}
+\noindent\begin{minipage}{\linewidth}
+\begin{lstlisting}[
+    style=bash,
+    otherkeywords={user,repo},
+    emph={user,repo},
+    emphstyle={\color{lsthilite}}
+]
+showyourwork setup user/repo
+\end{lstlisting}
+\end{minipage}
+
+\noindent where \texttt{\color{lsthilite}user} and \texttt{\color{lsthilite}repo} are the user's GitHub handle and the repository name, respectively. 
+After the user answers a few prompts, \syw will set up a local \texttt{git} repository \texttt{\color{lsthilite}repo} with the correct structure and placeholder files (see \S\ref{sec:usage:struct}).
+The article may then be built by running\\
+
+\noindent\begin{minipage}{\linewidth}
+\begin{lstlisting}[
+    style=bash
+]
+showyourwork
+\end{lstlisting}
+\end{minipage}
+
+\noindent from the root of the repository.
+
+\subsection{Repository structure}
+\label{sec:usage:struct}
 %
-\begin{figure}[ht!]
+\begin{figure}[p!]
     \begin{centering}
-        \includegraphics[width=0.25\linewidth]{figures/tree.pdf}
+        \includegraphics[width=0.8\linewidth]{figures/tree.pdf}
         \caption{
-            The basic repository structure for an open source scientific article built with \texttt{showyourwork!}.
+            The basic repository structure for an open source scientific article built with \syw.
             This figure was automatically generated from the \texttt{TikZ} code in \texttt{src/scripts/tree.tex} by specifying a custom command in \texttt{showyourwork.yml}.
@@
 %
-Figure~\ref{fig:tree} shows the basic directory structure for a repository instantiated from \texttt{showyourwork-template}. 
-The main components are:
-\begin{itemize}
-    \item \texttt{.github/workflows}: Contains configuration files for the \texttt{GitHub Actions} workflows, with instructions on how to set up the virtual environment, checkout the repository, and invoke the \texttt{showyourwork-action} to build and publish the article PDF.
-    \item \texttt{src/data}: Contains programmatically generated (or downloaded) datasets and dependencies that are not tracked by \texttt{git}.
-    \item \texttt{src/scripts}: Contains all of the scripts and auxiliary code needed to generate the article figures.
-    \item \texttt{src/static}: Contains miscellaneous files (usually figures) that are tracked by \texttt{git}.
-    These may include photographs, flowcharts, or other figures that cannot be programmatically generated.
-    \item \texttt{src/tex}: Contains the article manuscript and other auxiliary \texttt{TeX} files, such as the bibliography.
-    \item \texttt{Snakefile}: A file containing the rules for the \texttt{Snakemake} workflow.
-    By default, it simply imports all of the rules defined in \texttt{showyourwork/workflow/Snakefile}, but users can edit this file to add new rules or customize existing rules.
-    \item \texttt{environment.yml}: The \texttt{conda} environment file specifying all of the direct software dependencies of the workflow.
-    \item \texttt{showyourwork.yml}: The main configuration file for the workflow, where users can specify figure and dataset dependencies, instructions for downloading datasets from \texttt{Zenodo}.
-\end{itemize}
+Figure~\ref{fig:tree} shows the basic directory structure for a \syw article repository as of version \texttt{0.3.0}.
+Repositories are comprised of a configuration files at the root level and a directory called \texttt{src} containing the manuscript files and all of the the code and workflow scripts needed to render the final article PDF.
+
+\section{How it works}
+\label{sec:how-it-works}
+Coming soon.
 
@@
 
-\begin{figure}[ht!]
+In this section, we showcase a few projects based on \syw to illustrate how the workflow can facilitate the development and dissemination of open source scientific articles.
+
+The most fundamental feature of \syw is the automatic generation of the figures in a paper, such as Figure~\ref{fig:eccentricity}, which we reproduce from \citet{Wagg2022}.
+This figure was generated from the script \href{\fileurl{src/scripts/eccentricity.py}}{\texttt{src/scripts/eccentricity.py}} and has only a single other dependency: the \texttt{conda} environment file \href{\fileurl{environment.yml}}{\texttt{environment.yml}} (see Figure~\ref{fig:dag}).
+
+\begin{figure}[htp]
     \begin{centering}
@@
 
-\begin{figure}[ht!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/luhman16b.pdf}
-        \caption{
-            16 \emph{CRIRES} spectra of WISE 1049-5319B spanning a full rotation period of the brown dwarf; adapted from Figure 14 in \citet{Luger2021} and based on data from \citet{Crossfield2014}.
-            This figure was automatically generated from the script \texttt{src/scripts/luhman16b.py} and a dataset downloaded from \texttt{Zenodo}.
-        }
-        \label{fig:luhman16b}
-        \script{luhman16b.py}
-    \end{centering}
-\end{figure}
+% \begin{figure}[htp]
+%     \begin{centering}
+%         \includegraphics[width=\linewidth]{figures/luhman16b.pdf}
+%         \caption{
+%             16 \emph{CRIRES} spectra of WISE 1049-5319B spanning a full rotation period of the brown dwarf; adapted from Figure 14 in \citet{Luger2021} and based on data from \citet{Crossfield2014}.
+%             This figure was automatically generated from the script \texttt{src/scripts/luhman16b.py} and a dataset downloaded from \texttt{Zenodo}.
+%         }
+%         \label{fig:luhman16b}
+%         \script{luhman16b.py}
+%     \end{centering}
+% \end{figure}
 
-\begin{figure}[ht!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/two_moons.pdf}
-        \caption{
-            A normalizing flow demonstrated on the two moons data set from \texttt{scikit-learn};
-            reproduced from Figure 1 in \citet{Crenshaw2022}.
-            This figure was automatically generated from the script \texttt{src/scripts/two\_moons.py}
-            and an intermediate dataset that was automatically cached on \texttt{Zenodo}.
-        }
-        \label{fig:two_moons}
-        \script{two_moons.py}
-    \end{centering}
-\end{figure}
+% \begin{figure}[htp]
+%     \begin{centering}
+%         \includegraphics[width=\linewidth]{figures/two_moons.pdf}
+%         \caption{
+%             A normalizing flow demonstrated on the two moons data set from \texttt{scikit-learn};
+%             reproduced from Figure 1 in \citet{Crenshaw2022}.
+%             This figure was automatically generated from the script \texttt{src/scripts/two\_moons.py}
+%             and an intermediate dataset that was automatically cached on \texttt{Zenodo}.
+%         }
+%         \label{fig:two_moons}
+%         \script{two_moons.py}
+%     \end{centering}
+% \end{figure}
 
-\section{Integration with Zenodo}
-\label{sec:zenodo}
-%
-Coming soon.
+% \section{Integration with Zenodo}
+% \label{sec:zenodo}
+% %
+% Coming soon.
 
-\section{This paper}
+% \section{This paper}
 
-\begin{figure}[ht!]
+\begin{figure}[htp]
     \begin{centering}

### 2022-08-01 src/tex/ms.tex
more text

@@
 \usepackage{tikz}
+\usepackage[figuresright]{rotating}
 
@@
 \newcommand\syw{\texttt{showyourwork}\xspace}
-\newcommand\fileurl[1]{https://github.com/showyourwork/showyourwork-paper/blob/\GitHubSHA/#1}
+\newcommand\repourl{https://github.com/showyourwork/showyourwork-paper}
+\newcommand\commiturl{\repourl/tree/\GitHubSHA}
+\newcommand\fileurl[1]{\repourl/blob/\GitHubSHA/#1}
 
@@
 
-\syw was designed to tackle these three issues, making it easy to develop, publish, and distribute truly open and reproducible research papers in astronomy and other scientific disciplines. 
-At its core, it is a command-line tool that builds papers from a set of instructions contained in a \texttt{GitHub} repository and organized into \texttt{TeX} files, figure scripts, pipeline files, and configuration/specifications files.
+\begin{figure}[t!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/overview.pdf}
+        \caption{
+            Overview of the \syw workflow for a scientific article.
+            All code and instructions to compile the article exist within a GitHub repository (top center), optionally synced with an Overleaf project (top right).
+            Upon every commit, a GitHub Action is triggered to build the article in an isolated environment.
+            Scripts are executed to generate figures and other workflow output (bottom center), optionally downloading version-controlled datasets from Zenodo (top left), and optionally caching intermediate results on Zenodo Sandbox (bottom left).
+            Finally, the compiled article PDF, alongside an arXiv-compatible tarball, are generated and pushed to a special branch on the GitHub repository.
+        }
+        \label{fig:overview}
+    \end{centering}
+\end{figure}
+
+\syw was designed to tackle these three issues, making it easy for authors to develop, publish, and distribute truly open and reproducible research papers in astronomy and other scientific disciplines.
+At its core, it is a command-line tool that builds papers from a set of instructions contained in a \texttt{GitHub} repository and organized into \texttt{TeX} files, figure scripts, pipeline files, and configuration/specifications files (see Figure~\ref{fig:overview}).
 Every time the user pushes a new commit to \texttt{GitHub}, the article is automatically built on the cloud using \texttt{GitHub Actions} and the resulting PDF is pushed to a separate branch of the repository.
@@
 These instructions are for version \texttt{0.3.0} of the code, the current version at the time of writing (July 2022) and are subject to change in future releases.
-For more details, including custom commands, settings, examples, and troubleshooting tops, please refer to the documentation for the specific version of \syw at \url{https://show-your.work}.
+For more details, including custom commands, settings, examples, and troubleshooting tips, please refer to the documentation for the specific version of \syw at \url{https://show-your.work}.
 
@@
 ]
-python -m pip install -U showyourwork
+pip install -U showyourwork
 \end{lstlisting}
@@
 cd showyourwork
-python -m pip install .
+python setup.py install .
 \end{lstlisting}
@@
 \label{sec:usage:reproduce}
-Any project based on \syw can be reproduced by cloning its \texttt{GitHub} repository and running \syw. For example, to reproduce this paper, run:\\
+Any project based on \syw can be reproduced by cloning its \texttt{GitHub} repository and running \syw. For example, to reproduce the exact version of this paper that you are currently reading, run:\\
 
@@
 \begin{lstlisting}[
-    style=bash
+    style=bash,
+    escapeinside={|}{|}
 ]
@@
 cd showyourwork-paper
+git checkout |\GitHubSHA|
 showyourwork
@@
             The basic repository structure for an open source scientific article built with \syw.
+            The article you are reading was generated from a repository with this exact structure; you can check it out \href{\commiturl}{here}.
             This figure was automatically generated from the \texttt{TikZ} code in \texttt{src/scripts/tree.tex} by specifying a custom command in \texttt{showyourwork.yml}.
@@
 
-\begin{figure}[htp]
+To establish dependencies between scripts and figures included in the TeX manuscript, users may provide the custom \texttt{\textbackslash script\{{\color{lsthilite}script}\}} command within the \texttt{figure} environment, where \texttt{\color{lsthilite}script} is the name of the script \syw should execute to generate the figure(s) within the current environment.
+Additional dependencies may be specified explicitly in the \texttt{showyourwork.yml} configuration file or implicitly via custom rules in the \texttt{Snakefile}.
+
+As a seconde example, consider Figure~\ref{fig:luhman16b}, which we reproduce from \citet{Luger2021}. 
+Unlike Figure~\ref{fig:eccentricity}, this figure has an external dependency: a Zenodo-hosted dataset containing the \emph{CRIRES} observations of the spectrum of a brown dwarf.
+Users simply specify the DOI of the dataset and the files they wish to make dependencies of a given figure in \texttt{showyourwork.yml}, and \syw will download the data as needed.
+
+Finally, Figure~\ref{fig:two_moons} is an example of a figure depending on an intermediate result that is cached on Zenodo Sandbox.
+
+\clearpage
+
+\begin{figure}[p!]
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/eccentricity.pdf}
+        \includegraphics[width=0.75\linewidth]{figures/eccentricity.pdf}
         \caption{
@@
             This figure was automatically generated from the script \texttt{src/scripts/eccentricity.py}.
+            The GitHub icon in the margin is a clickable link pointing to the exact version of the script on GitHub used to produce this figure.
         }
@@
 
-% \begin{figure}[htp]
-%     \begin{centering}
-%         \includegraphics[width=\linewidth]{figures/luhman16b.pdf}
-%         \caption{
-%             16 \emph{CRIRES} spectra of WISE 1049-5319B spanning a full rotation period of the brown dwarf; adapted from Figure 14 in \citet{Luger2021} and based on data from \citet{Crossfield2014}.
-%             This figure was automatically generated from the script \texttt{src/scripts/luhman16b.py} and a dataset downloaded from \texttt{Zenodo}.
-%         }
-%         \label{fig:luhman16b}
-%         \script{luhman16b.py}
-%     \end{centering}
-% \end{figure}
+\begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=0.75\linewidth]{figures/luhman16b.pdf}
+        \caption{
+            16 \emph{CRIRES} spectra of WISE 1049-5319B spanning a full rotation period of the brown dwarf; adapted from Figure 14 in \citet{Luger2021} and based on data from \citet{Crossfield2014}.
+            This figure was automatically generated from the script \texttt{src/scripts/luhman16b.py} and a dataset downloaded from \texttt{Zenodo}.
+            In addition to the GitHub icon linking to the script, this figure also has a dataset icon linking to the Zenodo deposit that hosts the data needed to generate it.
+        }
+        \label{fig:luhman16b}
+        \script{luhman16b.py}
+    \end{centering}
+\end{figure}
 
-% \begin{figure}[htp]
-%     \begin{centering}
-%         \includegraphics[width=\linewidth]{figures/two_moons.pdf}
-%         \caption{
-%             A normalizing flow demonstrated on the two moons data set from \texttt{scikit-learn};
-%             reproduced from Figure 1 in \citet{Crenshaw2022}.
-%             This figure was automatically generated from the script \texttt{src/scripts/two\_moons.py}
-%             and an intermediate dataset that was automatically cached on \texttt{Zenodo}.
-%         }
-%         \label{fig:two_moons}
-%         \script{two_moons.py}
-%     \end{centering}
-% \end{figure}
+\begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=0.75\linewidth]{figures/two_moons.pdf}
+        \caption{
+            A normalizing flow demonstrated on the two moons data set from \texttt{scikit-learn};
+            reproduced from Figure 1 in \citet{Crenshaw2022}.
+            This figure was automatically generated from the script \texttt{src/scripts/two\_moons.py}
+            and an intermediate dataset that was automatically cached on \texttt{Zenodo}.
+        }
+        \label{fig:two_moons}
+        \script{two_moons.py}
+    \end{centering}
+\end{figure}
 
@@
 
-\begin{figure}[htp]
+\begin{sidewaysfigure}
     \begin{centering}
@@
     \end{centering}
-\end{figure}
+\end{sidewaysfigure}
 

### 2022-09-20 src/tex/ms.tex
more text, sections, placeholders

@@
 \usepackage[figuresright]{rotating}
+
+% Placeholders
+\newcommand\VERSION{0.3.1}
+\newcommand\MONTHYEAR{September 2022}
 
@@
 
+% Dev & review
+\newcommand\xxx[1]{{\color{red}#1}}
+\newcommand\needscite{{\color{red}(citation needed)}}
+
 % Other stuff
@@
 
-% Abstract with filler text
+%
 \begin{abstract}
@@
 
-% Main body with filler text
-\section{Introduction}
-\label{sec:intro}
+%
+\section{Three arguments for reproducibility}
+\label{sec:args}
+\xxx{Short intro here. I can think of three big ones, but there are perhaps many more.}
+
+% 1/3
+\subsection{Ensuring the validity of results}
+\label{sec:args:validity}
 As astronomical research software becomes increasingly more complex, and as research results become increasingly more interdependent, it becomes ever more challenging to ensure the validity and correctness of results published in the literature.
@@
 Checking all of the results in a paper would require the painstaking and methodical review of all of the paper's methods---which usually means scrutinizing all of the code used to generate the figures, tables, and other quantities in the paper.
+%
+\xxx{Any stats on how much time a typical referee spends on reviewing a paper? Would be nice to back all this up with some numbers.}
+%
+\xxx{We could also look for papers with erroneous results that propagated outwards in the literature because some big mistake made it past peer review. Anyone know of any classic examples?}
+%
 In practice, this is virtually impossible for three reasons:
-
+%
 \begin{enumerate}
@@
     %
-    \item The majority of astronomical code is not open source and simply cannot be vetted by third parties. 
-    While there has been a marked increase in the number of open source astronomical tools in recent years (e.g., \texttt{astropy}, \texttt{exoplanet}, \texttt{emcee}, \texttt{exofast}...), most code associated with the generation of the results in individual papers is not open source; readers are often expected to take it on faith that there are no bugs in that code, or that the code works exactly as described in the text, with no pitfalls or missing details.
+    \item The majority of astronomical code is not open source and simply cannot be vetted by third parties \needscite. 
+    While there has been a marked increase in the number of open source astronomical tools in recent years (e.g., \texttt{astropy}, \texttt{exoplanet}, \texttt{emcee}, \texttt{exofast}...), most code associated with the generation of the results in individual papers is not open source \needscite; readers are often expected to take it on faith that there are no bugs in that code, or that the code works exactly as described in the text, with no pitfalls or missing details.
     Even when the code is made publicly available, e.g., by being published on \texttt{GitHub}, it is often not documented sufficiently to enable one to execute it and reproduce the paper's results out-of-the-box.
@@
 \end{enumerate}
+%
+\xxx{A few sentences here on how an easily reproducible article could help with all this.}
+
+% 2/3
+\subsection{Reducing duplication of effort}
+\label{sec:args:duplication}
+\xxx{We shouldn't have to ever reinvent the wheel. Astronomy should be collaborative. Time saved on duplicated effort can be invested in moving the field forward rather than always playing catch-up.}
+%
+\xxx{Perhaps some stats on CPU usage in the field, and how reproducibility can help?}
+%
+\xxx{Can also talk about open data here; e.g., telescope time is super competitive; we should make it easy for others to use our data, both raw and processed.}
+
+% 3/3
+\subsection{Promoting equity and inclusivity}
+\label{sec:args:dei}
+\xxx{Proprietary legacy code is antithetical to DEI.
+``Source code available upon request'' is antithetical to DEI.
+``My code is on my website'' is antithetical to DEI.
+It's 2022, FFS.
+We need to do everything we can to make astronomy open to everyone.}
+
+\section{Current approaches to reproducibility}
+\label{sec:intro:curr}
+\xxx{Discuss code links in \citet{Luger2019,Luger2021a,Luger2021b}, and how they have caught on, e.g., \citet{Paillas2022}.} 
+%
+\xxx{Give a detailed overview of reproducibility in astronomy; \href{https://maneage.org/pdf/slides-intro.pdf}{this page} has some nice resources.
+Look at reviews by Harlan Krumholz in medicine.
+Talk about \texttt{\href{https://maneage.org}{maneage}}.}
+%
+
+\section{This paper: the \showyourwork workflow}
+\label{sec:intro:syw}
+This paper introduces \syw, a workflow designed to make it easy for authors to develop, publish, and distribute open and reproducible research papers in astronomy and other scientific disciplines. 
+At the highest level, \syw is a command-line tool that builds papers from a set of instructions contained in a version-controlled repository and organized into manuscript files, scripts, pipeline files, and configuration/specifications files (see Figure~\ref{fig:overview}).
+Every time the user makes changes to any of the files in the repository, the article is automatically re-built on the cloud and made publicly available on the remote repository.
+The build step---which installs the required software, generates all figures and other procedural output from scratch (with intelligent caching), and compiles the final article in an isolated build environment---acts as a unit test for the paper.
+If it passes, the paper is (by definition) reproducible.
 
@@
             Overview of the \syw workflow for a scientific article.
-            All code and instructions to compile the article exist within a GitHub repository (top center), optionally synced with an Overleaf project (top right).
-            Upon every commit, a GitHub Action is triggered to build the article in an isolated environment.
+            All code and instructions to compile the article exist within a \texttt{GitHub} repository (top center), optionally synced with an \texttt{Overleaf} project (top right).
+            Upon every commit, a \texttt{GitHub} Action is triggered to build the article in an isolated environment.
             Scripts are executed to generate figures and other workflow output (bottom center), optionally downloading version-controlled datasets from Zenodo (top left), and optionally caching intermediate results on Zenodo Sandbox (bottom left).
-            Finally, the compiled article PDF, alongside an arXiv-compatible tarball, are generated and pushed to a special branch on the GitHub repository.
+            Finally, the compiled article \texttt{.pdf} file, alongside an arXiv-compatible tarball, are generated and pushed to a special branch on the \texttt{GitHub} repository.
         }
@@
 
-\syw was designed to tackle these three issues, making it easy for authors to develop, publish, and distribute truly open and reproducible research papers in astronomy and other scientific disciplines.
-At its core, it is a command-line tool that builds papers from a set of instructions contained in a \texttt{GitHub} repository and organized into \texttt{TeX} files, figure scripts, pipeline files, and configuration/specifications files (see Figure~\ref{fig:overview}).
-Every time the user pushes a new commit to \texttt{GitHub}, the article is automatically built on the cloud using \texttt{GitHub Actions} and the resulting PDF is pushed to a separate branch of the repository.
-The build step---which sets up the conda environment, generates all figures from scratch (with intelligent caching), and compiles the PDF---acts as a unit test for the paper. 
-If it passes, the paper is (by definition) reproducible.
-
-\syw works out of the box for simple projects, in which each figure is generated by running a given script. 
-But it also works for more complicated pipelines, such as projects that depend on many intermediate steps or those that require running expensive simulations on clusters. 
+The ideas presented here are not new; nor are the ways in which they are implemented.
+Instead, the main goal of \syw is to make developing---and using---reproducible scientific articles as easy as possible.
+\syw works out of the box for simple projects, in which each figure in the article can be generated by running a given script. 
+But it also works for more complicated pipelines, such as projects that depend on many intermediate steps or those that require running expensive simulations. 
 The workflow interfaces directly with \texttt{Zenodo}, allowing users to automatically upload the results of simulations so that expensive build steps can be bypassed on the cloud. 
@@
 
-Papers that use \syw can be reproduced by cloning the associated repository and running \syw. 
-Such papers (like this one!) include clickable icons next to each of their figures linking to (1) the exact version of the script on \texttt{GitHub} used to generate them and (2) the exact version(s) of the \texttt{Zenodo}-hosted dataset(s) used in their creation.
+Papers that use \syw can be reproduced by downloading the associated repository and running the \syw command-line tool. 
+Such papers (like this one!) include clickable icons next to each of their figures linking to (1) the exact version of the script used to generate them and (2) the exact version(s) of the dataset(s) used in their creation.
 
@@
 In this section we provide basic, high-level instructions on how to install and use \syw.
-These instructions are for version \texttt{0.3.0} of the code, the current version at the time of writing (July 2022) and are subject to change in future releases.
-For more details, including custom commands, settings, examples, and troubleshooting tips, please refer to the documentation for the specific version of \syw at \url{https://show-your.work}.
+These instructions are for version \texttt{\VERSION} of the code, the current version at the time of writing (\MONTHYEAR) and are subject to change in future releases.
+For more details, including custom commands, settings, examples, and troubleshooting tips, please refer to the documentation for the specific version of \syw.
 
@@
 \syw requires the \texttt{conda} package manager\footnote{\url{https://www.anaconda.com/products/distribution}} and is currently tested only on Unix-like operating systems (such as Linux, Ubuntu, or MacOS).
-Users must also have access to a \texttt{GitHub} account; other \texttt{git} platforms are not currently supported.
+Users must also have access to a \texttt{GitHub}\footnote{\url{https://www.github.com}} account; other \texttt{git} platforms are not currently supported.
 Note that users do \emph{not} need a local installation of a \texttt{TeX} distribution, as \syw uses the \texttt{conda}-managed \texttt{tectonic} package to compile articles.
@@
 
-\noindent This will set up a custom \texttt{conda} environment for the workflow, download the required datasets from \texttt{Zenodo}, build all of the figures, and generate a PDF identical to this one.
+\noindent This will set up a custom \texttt{conda} environment for the workflow, download the required datasets from \texttt{Zenodo}, build all of the figures, and generate a \texttt{.pdf} file identical to this one.
 
@@
 
-\noindent where \texttt{\color{lsthilite}user} and \texttt{\color{lsthilite}repo} are the user's GitHub handle and the repository name, respectively. 
+\noindent where \texttt{\color{lsthilite}user} and \texttt{\color{lsthilite}repo} are the user's \texttt{GitHub} handle and the repository name, respectively. 
 After the user answers a few prompts, \syw will set up a local \texttt{git} repository \texttt{\color{lsthilite}repo} with the correct structure and placeholder files (see \S\ref{sec:usage:struct}).
@@
 %
-Figure~\ref{fig:tree} shows the basic directory structure for a \syw article repository as of version \texttt{0.3.0}.
-Repositories are comprised of a configuration files at the root level and a directory called \texttt{src} containing the manuscript files and all of the the code and workflow scripts needed to render the final article PDF.
+Figure~\ref{fig:tree} shows the basic directory structure for a \syw article repository as of version \texttt{\VERSION}.
+Repositories are comprised of configuration files at the root level and a directory called \texttt{src} containing the manuscript files and all of the the code and workflow scripts needed to render the final article \texttt{.pdf} file.
+%
+\xxx{More details here.}
 
@@
 \label{sec:how-it-works}
-Coming soon.
+\xxx{Discuss how things are actually implemented.
+Talk about the dependence on \texttt{Snakemake} \citep{Molder2021} and \texttt{tectonic}\footnote{\url{https://tectonic-typesetting.github.io}}.
+Discuss the integration with \texttt{Zenodo} for both static datasets and cached datasets.
+Discuss integration with \texttt{Overleaf}.}
 
@@
 \label{sec:examples}
-
 In this section, we showcase a few projects based on \syw to illustrate how the workflow can facilitate the development and dissemination of open source scientific articles.
@@
 
-As a seconde example, consider Figure~\ref{fig:luhman16b}, which we reproduce from \citet{Luger2021}. 
+As a seconde example, consider Figure~\ref{fig:luhman16b}, which we reproduce from \citet{Luger2021c}. 
 Unlike Figure~\ref{fig:eccentricity}, this figure has an external dependency: a Zenodo-hosted dataset containing the \emph{CRIRES} observations of the spectrum of a brown dwarf.
@@
 
-Finally, Figure~\ref{fig:two_moons} is an example of a figure depending on an intermediate result that is cached on Zenodo Sandbox.
+Figure~\ref{fig:two_moons} is an example of a figure depending on an intermediate result that is cached on Zenodo Sandbox.
+\xxx{More details.}
 
+\xxx{Discuss Table~\ref{tab:variable} and variable output.}
+
+\xxx{Discuss Figure~\ref{fig:dag} and this paper as a whole as a meta-example.}
+
+\xxx{Finally, cite a bunch of papers here that already use showyourwork and showcase its various features.}
+
+\section{Current issues and future work}
+\label{sec:future}
+\xxx{This is a work in progress.
+Currently focused primarily on short-term reproducibility; discuss the various issues that arise from relying on \texttt{GitHub}, \texttt{conda}, \texttt{pip}, etc.
+Broken links will be an issue.
+Conda environments are not impermeable.
+Currently difficult (impossible?) to run stuff on a cluster.
+Doesn't play nice with journals.
+Anything  else?}
+
+\section{Conclusion}
+\label{sec:conclusion}
+\xxx{Stuff here. showyourwork is a community project -- please contribute!}
+
+% DEBUG -- place figures inline with text
 \clearpage
@@
             This figure was automatically generated from the script \texttt{src/scripts/eccentricity.py}.
-            The GitHub icon in the margin is a clickable link pointing to the exact version of the script on GitHub used to produce this figure.
+            The \texttt{GitHub} icon in the margin is a clickable link pointing to the exact version of the script on \texttt{GitHub} used to produce this figure.
         }
@@
         \caption{
-            16 \emph{CRIRES} spectra of WISE 1049-5319B spanning a full rotation period of the brown dwarf; adapted from Figure 14 in \citet{Luger2021} and based on data from \citet{Crossfield2014}.
+            16 \emph{CRIRES} spectra of WISE 1049-5319B spanning a full rotation period of the brown dwarf; adapted from Figure 14 in \citet{Luger2021c} and based on data from \citet{Crossfield2014}.
             This figure was automatically generated from the script \texttt{src/scripts/luhman16b.py} and a dataset downloaded from \texttt{Zenodo}.
-            In addition to the GitHub icon linking to the script, this figure also has a dataset icon linking to the Zenodo deposit that hosts the data needed to generate it.
+            In addition to the \texttt{GitHub} icon linking to the script, this figure also has a dataset icon linking to the Zenodo deposit that hosts the data needed to generate it.
         }
@@
             and an intermediate dataset that was automatically cached on \texttt{Zenodo}.
+            \xxx{@jfcrenshaw: is it ok for us to reproduce this figure of yours?}
         }
@@
 
-% \section{Integration with Zenodo}
-% \label{sec:zenodo}
-% %
-% Coming soon.
-
-% \section{This paper}
+\begin{table}[p!]
+    \begin{center}
+        \begin{tabular}{@{}l|l@{}}
+            \hline
+            Name & Representation \\
+            \hline
+            \variable{output/kernels.tex}
+        \end{tabular}
+    \end{center}
+    \caption{A table with programmatically-generated output. Reproduced from Table 1 in \citet{Aigrain2022}. \xxx{@dfm: is it ok for us to reproduce this table of yours?}}
+    \label{tab:variable}
+\end{table}
 
@@
 The \texttt{src/static} directory is reserved for figures that are not programmatically generated and simply get copied over to the output directory at compile time.
+            \xxx{TODO: Regenerate me!}
         }

### 2022-09-20 src/scripts/kernels.py

@@ -1,0 +1,30 @@
+from sympy import *
+import paths
+
+# Free parameters
+alpha, beta, gamma, Gamma, lam, tau = symbols(
+    r"\alpha \beta \gamma \Gamma \lambda \tau"
+)
+
+# Define the kernels
+kernels = {
+    "Constant": alpha**2,
+    "Squared Exponential": exp(-((tau / lam) ** 2) / 2),
+    "Exponential": exp(-(tau / lam)),
+    r"Mat\'ern 3/2": (1 + sqrt(3) * tau / lam) * exp(-sqrt(3) * tau / lam),
+    r"Mat\'ern 5/2": (1 + sqrt(5) * tau / lam + 5 * (tau / lam) ** 2 / 3)
+    * exp(-sqrt(5) * tau / lam),
+    "Rational Quadratic": (1 + tau**2 / (2 * gamma * lam**2)) ** (-gamma),
+    "Cosine": cos(2 * pi * tau / lam),
+    "Sine Squared Exponential": exp(-Gamma * sin(pi * tau / lam) ** 2),
+    "Stochastic Harmonic Oscillator": cos(sqrt(1 - beta**2) * tau / lam)
+    + beta / sqrt(1 - beta**2) * sin(sqrt(1 - beta**2) * tau / lam),
+}
+
+# Write all of them to the LaTeX table
+kernels = (r"\\" + "\n\t").join(
+    name + " & " + "$" + latex(expr) + "$" for (name, expr) in kernels.items()
+)
+with open(paths.output / "kernels.tex", "w") as f:
+    f.write(kernels)
+    f.write(r"\\\hline")

### 2022-09-21 src/tex/ms.tex
dynamic tables

@@
 % Define document class
-\documentclass[modern]{aastex631}
+\documentclass{aastex631}
 
@@
 
-\begin{table}[p!]
+\begin{table}
     \begin{center}
@@
     \end{center}
-    \caption{A table with programmatically-generated output. Reproduced from Table 1 in \citet{Aigrain2022}. \xxx{@dfm: is it ok for us to reproduce this table of yours?}}
+    \caption{The functional forms of various commonly used Gaussian process kernels; reproduced from Table~1 in \citet{Aigrain2022}.
+    The contents of this table are programmatically generated; the kernels are defined as \texttt{sympy} expressions and rendered into \texttt{TeX} form in the script \texttt{src/scripts/kernels.py}.
+    The autogenerated \texttt{GitHub} icon in the margin links to the rule in the \texttt{Snakefile} that runs that script.
+    \xxx{@dfm: is it ok for us to reproduce this table of yours?}}
     \label{tab:variable}

### 2022-09-21 src/scripts/kernels.py

@@ -6,7 +6,8 @@ alpha, beta, gamma, Gamma, lam, tau = symbols(
     r"\alpha \beta \gamma \Gamma \lambda \tau"
 )
 
-# Define the kernels
+# Define the kernels. Changing anything here will automatically
+# update the corresponding table in the article.
 kernels = {
     "Constant": alpha**2,
     "Squared Exponential": exp(-((tau / lam) ** 2) / 2),
@@ -22,9 +23,8 @@ kernels = {
 }
 
 # Write all of them to the LaTeX table
-kernels = (r"\\" + "\n\t").join(
+kernels = (r"\\" + "\n").join(
     name + " & " + "$" + latex(expr) + "$" for (name, expr) in kernels.items()
 )
 with open(paths.output / "kernels.tex", "w") as f:
     f.write(kernels)
-    f.write(r"\\\hline")

### 2022-09-22 src/tex/ms.tex
more text

@@
 
-% Import showyourwork
+% Imports
 \usepackage{showyourwork}
-
-% Other imports
 \usepackage{etoolbox}
@@
 \usepackage[figuresright]{rotating}
+\usepackage{ifthen}
 
 % Placeholders
-\newcommand\VERSION{0.3.1}
+\newcommand\VERSION{\texttt{0.3.1}\xspace}
 \newcommand\MONTHYEAR{September 2022}
+
+% Dev & review
+\newcommand\xxx[1]{{\color{red}#1}}
+\newcommand\needscite{{\color{red}(citation needed)}}
 
@@
 \definecolor{codebkg}{rgb}{0.89,0.89,0.89}
-\colorlet{lsthilite}{fancyblue}
+\colorlet{lsthilite}{blue}
 
@@
 
-% Dev & review
-\newcommand\xxx[1]{{\color{red}#1}}
-\newcommand\needscite{{\color{red}(citation needed)}}
+% Declare products, tools, services, etc. with optional
+% hyperlinks that display only the first time we mention them
+\newcommand{\newproduct}[2][]{%
+    \ifthenelse{\equal{#1}{}}{%
+        \expandafter\def\csname #2\endcsname{\texttt{#2}\xspace}%
+    }{%
+        \expandafter\def\csname #2showlink\endcsname{1}%
+        \expandafter\newcommand\csname #2\endcsname{%
+            \ifnum\expandafter\csname #2showlink\endcsname=1
+                \global\expandafter\def\csname #2showlink\endcsname{0}%
+                \href{#1}{\texttt{#2}}\xspace%
+            \else
+                \texttt{#2}\xspace%
+            \fi
+        }%
+    }%
+}
+\newproduct[https://www.github.com]{GitHub}
+\newproduct[https://www.overleaf.com]{Overleaf} 
+\newproduct[https://zenodo.org]{Zenodo} 
+\newproduct[https://sandbox.zenodo.org]{ZenodoSandbox} 
+\newproduct[https://www.anaconda.com/products/distribution]{conda} 
+\newproduct[https://tectonic-typesetting.github.io]{tectonic} 
+\newproduct[https://snakemake.github.io]{snakemake} 
+\newproduct[https://maneage.org]{maneage} 
+\newproduct{git}
+\newproduct{Python}
+\newproduct{pip}
+\newproduct{TikZ}
+\newproduct{astropy}
+\newproduct{exoplanet}
+\newproduct{exofast}
+\newproduct{emcee}
+\newproduct{sympy}
 
-% Other stuff
+% Other stylized product names
 \newcommand\syw{\texttt{showyourwork}\xspace}
-\newcommand\repourl{https://github.com/showyourwork/showyourwork-paper}
-\newcommand\commiturl{\repourl/tree/\GitHubSHA}
-\newcommand\fileurl[1]{\repourl/blob/\GitHubSHA/#1}
+\newcommand\pdf{\texttt{.pdf}\xspace}
+\newcommand\scikitlearn{\texttt{scikit-learn}\xspace}
+\let\oldTeX\TeX\renewcommand\TeX{\oldTeX\xspace}
+
+% Repo links
+\newcommand\repoargurl{https://github.com/showyourwork/showyourwork-paper}
+\newcommand\commiturl{\repoargurl/tree/\GitHubSHA}
+\newcommand\fileurl[1]{\repoargurl/blob/\GitHubSHA/#1}
+\newcommand\repoargfile[1]{\href{\fileurl{#1}}{\texttt{#1}\xspace}}
+
+% Syntax
+\newcommand\userarg{\texttt{\color{lsthilite}user}\xspace}
+\newcommand\repoarg{\texttt{\color{lsthilite}repo}\xspace}
+\newcommand\figenv{\texttt{figure}\xspace}
+\newcommand\scriptcmd{\texttt{\textbackslash script\{{\color{lsthilite}script}\}}\xspace}
+\newcommand\scriptarg{\texttt{\color{lsthilite}script}\xspace}
 
@@
 \label{sec:args}
-\xxx{Short intro here. I can think of three big ones, but there are perhaps many more.}
+\xxx{Short intro here. I can think of three big arguments for reproducibility, but there are likely many more.}
 
@@
     \item The majority of astronomical code is not open source and simply cannot be vetted by third parties \needscite. 
-    While there has been a marked increase in the number of open source astronomical tools in recent years (e.g., \texttt{astropy}, \texttt{exoplanet}, \texttt{emcee}, \texttt{exofast}...), most code associated with the generation of the results in individual papers is not open source \needscite; readers are often expected to take it on faith that there are no bugs in that code, or that the code works exactly as described in the text, with no pitfalls or missing details.
-    Even when the code is made publicly available, e.g., by being published on \texttt{GitHub}, it is often not documented sufficiently to enable one to execute it and reproduce the paper's results out-of-the-box.
+    While there has been a marked increase in the number of open source astronomical tools in recent years (e.g., \astropy, \exoplanet, \emcee, \exofast...), most code associated with the generation of the results in individual papers is not open source \needscite; readers are often expected to take it on faith that there are no bugs in that code, or that the code works exactly as described in the text, with no pitfalls or missing details.
+    Even when the code is made publicly available, e.g., by being published on \GitHub, it is often not documented sufficiently to enable one to execute it and reproduce the paper's results out-of-the-box.
     And even with proper documentation, the code may require external dependencies, custom virtual environments, or access to closed-source datasets that make it difficult or impossible for a third party to replicate it.
@@
 Look at reviews by Harlan Krumholz in medicine.
-Talk about \texttt{\href{https://maneage.org}{maneage}}.}
+Talk about \maneage.}
 %
@@
             Overview of the \syw workflow for a scientific article.
-            All code and instructions to compile the article exist within a \texttt{GitHub} repository (top center), optionally synced with an \texttt{Overleaf} project (top right).
-            Upon every commit, a \texttt{GitHub} Action is triggered to build the article in an isolated environment.
+            All code and instructions to compile the article exist within a \GitHub repository (top center), optionally synced with an \Overleaf project (top right).
+            Upon every commit, a \GitHub Action is triggered to build the article in an isolated environment.
             Scripts are executed to generate figures and other workflow output (bottom center), optionally downloading version-controlled datasets from Zenodo (top left), and optionally caching intermediate results on Zenodo Sandbox (bottom left).
-            Finally, the compiled article \texttt{.pdf} file, alongside an arXiv-compatible tarball, are generated and pushed to a special branch on the \texttt{GitHub} repository.
+            Finally, the compiled article \pdf file, alongside an arXiv-compatible tarball, are generated and pushed to a special branch on the \GitHub repository.
         }
@@
 But it also works for more complicated pipelines, such as projects that depend on many intermediate steps or those that require running expensive simulations. 
-The workflow interfaces directly with \texttt{Zenodo}, allowing users to automatically upload the results of simulations so that expensive build steps can be bypassed on the cloud. 
+The workflow interfaces directly with \Zenodo, allowing users to automatically upload the results of simulations so that expensive build steps can be bypassed on the cloud. 
 In fact, most of the features under the hood are there to make the workflow as flexible and customizable as possible.
@@
 In this section we provide basic, high-level instructions on how to install and use \syw.
-These instructions are for version \texttt{\VERSION} of the code, the current version at the time of writing (\MONTHYEAR) and are subject to change in future releases.
+These instructions are for version \VERSION of the code, the current version at the time of writing (\MONTHYEAR) and are subject to change in future releases.
 For more details, including custom commands, settings, examples, and troubleshooting tips, please refer to the documentation for the specific version of \syw.
@@
 \label{sec:usage:prereq}
-\syw requires the \texttt{conda} package manager\footnote{\url{https://www.anaconda.com/products/distribution}} and is currently tested only on Unix-like operating systems (such as Linux, Ubuntu, or MacOS).
-Users must also have access to a \texttt{GitHub}\footnote{\url{https://www.github.com}} account; other \texttt{git} platforms are not currently supported.
-Note that users do \emph{not} need a local installation of a \texttt{TeX} distribution, as \syw uses the \texttt{conda}-managed \texttt{tectonic} package to compile articles.
+\syw requires the \conda package manager and is currently tested only on Unix-like operating systems (such as Linux, Ubuntu, or MacOS).
+Users must also have access to a \GitHub account; other \git platforms are not currently supported.
+Note that users do \emph{not} need a local installation of a \TeX distribution, as \syw uses the \conda-managed \tectonic package to compile articles.
 
@@
 \label{sec:usage:install}
-\syw can be installed with the \texttt{Python} package manager \texttt{pip}:\\
+\syw can be installed with the \Python package manager \pip:\\
 
@@
 
-\noindent (recommended) or from source on \texttt{GitHub}:\\
+\noindent (recommended) or from source on \GitHub:\\
 
@@
 \label{sec:usage:reproduce}
-Any project based on \syw can be reproduced by cloning its \texttt{GitHub} repository and running \syw. For example, to reproduce the exact version of this paper that you are currently reading, run:\\
+Any project based on \syw can be reproduced by cloning its \GitHub repository and running \syw. For example, to reproduce the exact version of this paper that you are currently reading, run:\\
 
@@
 
-\noindent This will set up a custom \texttt{conda} environment for the workflow, download the required datasets from \texttt{Zenodo}, build all of the figures, and generate a \texttt{.pdf} file identical to this one.
+\noindent This will set up a custom \conda environment for the workflow, download the required datasets from \Zenodo, build all of the figures, and generate a \pdf file identical to this one.
 
@@
 
-\noindent where \texttt{\color{lsthilite}user} and \texttt{\color{lsthilite}repo} are the user's \texttt{GitHub} handle and the repository name, respectively. 
-After the user answers a few prompts, \syw will set up a local \texttt{git} repository \texttt{\color{lsthilite}repo} with the correct structure and placeholder files (see \S\ref{sec:usage:struct}).
+\noindent where \userarg and \repoarg are the user's \GitHub handle and the repository name, respectively. 
+After the user answers a few prompts, \syw will set up a local \git repository \repoarg with the correct structure and placeholder files (see \S\ref{sec:usage:struct}).
 The article may then be built by running\\
@@
             The article you are reading was generated from a repository with this exact structure; you can check it out \href{\commiturl}{here}.
-            This figure was automatically generated from the \texttt{TikZ} code in \texttt{src/scripts/tree.tex} by specifying a custom command in \texttt{showyourwork.yml}.
+            This figure was automatically generated from the \TikZ code in \repoargfile{src/scripts/tree.tex} by specifying a custom command in \repoargfile{showyourwork.yml}.
         }
@@
 %
-Figure~\ref{fig:tree} shows the basic directory structure for a \syw article repository as of version \texttt{\VERSION}.
-Repositories are comprised of configuration files at the root level and a directory called \texttt{src} containing the manuscript files and all of the the code and workflow scripts needed to render the final article \texttt{.pdf} file.
+Figure~\ref{fig:tree} shows the basic directory structure for a \syw article repository as of version \VERSION{}.
+Repositories are comprised of configuration files at the root level and a directory called \repoargfile{src} containing the manuscript files and all of the the code and workflow scripts needed to render the final article \pdf file.
 %
@@
 \xxx{Discuss how things are actually implemented.
-Talk about the dependence on \texttt{Snakemake} \citep{Molder2021} and \texttt{tectonic}\footnote{\url{https://tectonic-typesetting.github.io}}.
-Discuss the integration with \texttt{Zenodo} for both static datasets and cached datasets.
-Discuss integration with \texttt{Overleaf}.}
+Talk about the dependence on \snakemake \citep{Molder2021} and \tectonic.
+Discuss the integration with \Zenodo for both static datasets and cached datasets.
+Discuss integration with \Overleaf.}
 
@@
 The most fundamental feature of \syw is the automatic generation of the figures in a paper, such as Figure~\ref{fig:eccentricity}, which we reproduce from \citet{Wagg2022}.
-This figure was generated from the script \href{\fileurl{src/scripts/eccentricity.py}}{\texttt{src/scripts/eccentricity.py}} and has only a single other dependency: the \texttt{conda} environment file \href{\fileurl{environment.yml}}{\texttt{environment.yml}} (see Figure~\ref{fig:dag}).
+This figure was generated from the script \repoargfile{src/scripts/eccentricity.py} and has only a single other dependency: the \conda environment file \repoargfile{environment.yml} (see Figure~\ref{fig:dag}).
 
-To establish dependencies between scripts and figures included in the TeX manuscript, users may provide the custom \texttt{\textbackslash script\{{\color{lsthilite}script}\}} command within the \texttt{figure} environment, where \texttt{\color{lsthilite}script} is the name of the script \syw should execute to generate the figure(s) within the current environment.
-Additional dependencies may be specified explicitly in the \texttt{showyourwork.yml} configuration file or implicitly via custom rules in the \texttt{Snakefile}.
+To establish dependencies between scripts and figures included in the TeX manuscript, users may provide the custom \scriptcmd command within the \figenv environment, where \scriptarg is the name of the script \syw should execute to generate the figure(s) within the current environment.
+Additional dependencies may be specified explicitly in the \repoargfile{showyourwork.yml} configuration file or implicitly via custom rules in the \repoargfile{Snakefile}.
 
@@
 Unlike Figure~\ref{fig:eccentricity}, this figure has an external dependency: a Zenodo-hosted dataset containing the \emph{CRIRES} observations of the spectrum of a brown dwarf.
-Users simply specify the DOI of the dataset and the files they wish to make dependencies of a given figure in \texttt{showyourwork.yml}, and \syw will download the data as needed.
+Users simply specify the DOI of the dataset and the files they wish to make dependencies of a given figure in \repoargfile{showyourwork.yml}, and \syw will download the data as needed.
 
@@
 \xxx{Discuss Table~\ref{tab:variable} and variable output.}
+Variable output can also occur inline.
+For instance, the following sentence is programmatically generated from the same script: \variable{output/SHO_value.tex} Note the icon in the margin that automatically links to the corresponding \snakemake rule.
 
@@
 \xxx{This is a work in progress.
-Currently focused primarily on short-term reproducibility; discuss the various issues that arise from relying on \texttt{GitHub}, \texttt{conda}, \texttt{pip}, etc.
+Currently focused primarily on short-term reproducibility; discuss the various issues that arise from relying on \GitHub, \conda, \pip, etc.
 Broken links will be an issue.
@@
             The effect of binary eccentricity on the detectability of a \emph{LISA} gravitational wave source; reproduced from Figure 3 in \citet{Wagg2022}. 
-            This figure was automatically generated from the script \texttt{src/scripts/eccentricity.py}.
-            The \texttt{GitHub} icon in the margin is a clickable link pointing to the exact version of the script on \texttt{GitHub} used to produce this figure.
+            This figure was automatically generated from the script \repoargfile{src/scripts/eccentricity.py}.
+            The \GitHub icon in the margin is a clickable link pointing to the exact version of the script on \GitHub used to produce this figure.
         }
@@
             16 \emph{CRIRES} spectra of WISE 1049-5319B spanning a full rotation period of the brown dwarf; adapted from Figure 14 in \citet{Luger2021c} and based on data from \citet{Crossfield2014}.
-            This figure was automatically generated from the script \texttt{src/scripts/luhman16b.py} and a dataset downloaded from \texttt{Zenodo}.
-            In addition to the \texttt{GitHub} icon linking to the script, this figure also has a dataset icon linking to the Zenodo deposit that hosts the data needed to generate it.
+            This figure was automatically generated from the script \repoargfile{src/scripts/luhman16b.py} and a dataset downloaded from \Zenodo.
+            In addition to the \GitHub icon linking to the script, this figure also has a dataset icon linking to the Zenodo deposit that hosts the data needed to generate it.
         }
@@
         \caption{
-            A normalizing flow demonstrated on the two moons data set from \texttt{scikit-learn};
+            A normalizing flow demonstrated on the two moons data set from \scikitlearn;
             reproduced from Figure 1 in \citet{Crenshaw2022}.
-            This figure was automatically generated from the script \texttt{src/scripts/two\_moons.py}
-            and an intermediate dataset that was automatically cached on \texttt{Zenodo}.
+            This figure was automatically generated from the script \repoargfile{src/scripts/two\_moons.py}
+            and an intermediate dataset that was automatically cached on \Zenodo.
             \xxx{@jfcrenshaw: is it ok for us to reproduce this figure of yours?}
@@
     \caption{The functional forms of various commonly used Gaussian process kernels; reproduced from Table~1 in \citet{Aigrain2022}.
-    The contents of this table are programmatically generated; the kernels are defined as \texttt{sympy} expressions and rendered into \texttt{TeX} form in the script \texttt{src/scripts/kernels.py}.
-    The autogenerated \texttt{GitHub} icon in the margin links to the rule in the \texttt{Snakefile} that runs that script.
+    The contents of this table are programmatically generated; the kernels are defined as \sympy expressions and rendered into \TeX form in the script \repoargfile{src/scripts/kernels.py}.
+    The autogenerated \GitHub icon in the margin links to the rule in the \repoargfile{Snakefile} that runs that script.
     \xxx{@dfm: is it ok for us to reproduce this table of yours?}}
@@
             A directed acyclic graph (DAG) showing the complete list of dependencies for the article. 
-            Scripts are shown in green, \texttt{Zenodo} deposits in blue, datasets in purple, and \texttt{TeX} files in red.
-            This figure is located in the \texttt{src/static} directory and, unlike the other figures in this article, is version controlled by \texttt{git}.
-The \texttt{src/static} directory is reserved for figures that are not programmatically generated and simply get copied over to the output directory at compile time.
+            Scripts are shown in green, \Zenodo deposits in blue, datasets in purple, and \TeX files in red.
+            This figure is located in the \repoargfile{src/static} directory and, unlike the other figures in this article, is version controlled by \git.
+The \repoargfile{src/static} directory is reserved for figures that are not programmatically generated and simply get copied over to the output directory at compile time.
             \xxx{TODO: Regenerate me!}

### 2022-09-22 src/scripts/kernels.py

@@ -23,8 +23,20 @@ kernels = {
 }
 
 # Write all of them to the LaTeX table
-kernels = (r"\\" + "\n").join(
-    name + " & " + "$" + latex(expr) + "$" for (name, expr) in kernels.items()
-)
 with open(paths.output / "kernels.tex", "w") as f:
-    f.write(kernels)
+    f.write(
+        (r"\\" + "\n").join(
+            name + " & " + "$" + latex(expr) + "$" for (name, expr) in kernels.items()
+        )
+    )
+
+
+with open(paths.output / "SHO_value.tex", "w") as f:
+    value = (
+        kernels["Stochastic Harmonic Oscillator"]
+        .subs({beta: 0.5, lam: 0.5, tau: 0.5})
+        .evalf()
+    )
+    f.write(
+        rf"The value of the Stochastic Harmonic Oscillator kernel for $\beta = \lambda = \tau = 0.5$ is {value:.5f}."
+    )

### 2022-09-22 src/tex/ms.tex
cuter

@@
 \xxx{Discuss Table~\ref{tab:variable} and variable output.}
-Variable output can also occur inline.
-For instance, the following sentence is programmatically generated from the same script: \variable{output/SHO_value.tex} Note the icon in the margin that automatically links to the corresponding \snakemake rule.
+Variable output can also occur inline. For instance, the following sentence is programmatically generated from the same script: 
+\variable{output/kernel_value.tex} 
+Note the icon in the margin that automatically links to the corresponding \snakemake rule, where users can easily change the values of the kernel parameters.
 

### 2022-09-22 src/scripts/kernels.py

@@ -30,13 +30,10 @@ with open(paths.output / "kernels.tex", "w") as f:
         )
     )
 
-
-with open(paths.output / "SHO_value.tex", "w") as f:
-    value = (
-        kernels["Stochastic Harmonic Oscillator"]
-        .subs({beta: 0.5, lam: 0.5, tau: 0.5})
-        .evalf()
-    )
-    f.write(
-        rf"The value of the Stochastic Harmonic Oscillator kernel for $\beta = \lambda = \tau = 0.5$ is {value:.5f}."
-    )
+params = dict(snakemake.params)
+kernel = params.pop("kernel")
+params = {eval(key): value for key, value in params.items()}
+with open(paths.output / "kernel_value.tex", "w") as f:
+    value = kernels[kernel].subs(params).evalf()
+    params = ",\,".join([f"{key} = {value:.2f}" for key, value in params.items()])
+    f.write(rf"The value of the {kernel} kernel for ${params}$ is ${value:.5f}$.")

### 2022-10-21 src/tex/ms.tex
todos

@@
 \usepackage{ifthen}
+\usepackage{xparse}
+\usepackage{stackengine}
 
@@
 % Dev & review
-\newcommand\xxx[1]{{\color{red}#1}}
 \newcommand\needscite{{\color{red}(citation needed)}}
+\DeclareDocumentCommand{\todo}{o o o o o o o o m}{%
+    {\color{red}#9}%
+    \marginpar{%
+        \raisebox{-0.5em}{%
+            \setstackgap{S}{0pt}%
+            \Shortstack[c]{
+                \IfValueT{#1}{\includegraphics[width=1.75em]{avatars/#1.png}\IfValueT{#2}{\includegraphics[width=1.75em]{avatars/#2.png}}}
+                \IfValueT{#3}{\includegraphics[width=1.75em]{avatars/#3.png}\IfValueT{#4}{\includegraphics[width=1.75em]{avatars/#4.png}}}
+                \IfValueT{#5}{\includegraphics[width=1.75em]{avatars/#5.png}\IfValueT{#6}{\includegraphics[width=1.75em]{avatars/#6.png}}}
+                \IfValueT{#7}{\includegraphics[width=1.75em]{avatars/#7.png}\IfValueT{#8}{\includegraphics[width=1.75em]{avatars/#8.png}}}
+            }%
+        }
+    }%
+}
 
@@
 \label{sec:args}
-\xxx{Short intro here. I can think of three big arguments for reproducibility, but there are likely many more.}
+\todo[rodluger][adrn][dfm][milescranmer][jfcrenshaw][mathren][katiebreivik][tomwagg]{Short intro here. I can think of three big arguments for reproducibility, but there are likely many more.}
 
@@
 %
-\xxx{Any stats on how much time a typical referee spends on reviewing a paper? Would be nice to back all this up with some numbers.}
-%
-\xxx{We could also look for papers with erroneous results that propagated outwards in the literature because some big mistake made it past peer review. Anyone know of any classic examples?}
+\todo[adrn][dfm][milescranmer][mathren]{
+    Any stats on how much time a typical referee spends on reviewing a paper? Would be nice to back all this up with some numbers.
+    We could also look for papers with erroneous results that propagated outwards in the literature because some big mistake made it past peer review. Anyone know of any classic examples?
+}
+
 %
@@
 %
-\xxx{A few sentences here on how an easily reproducible article could help with all this.}
+\todo[rodluger]{A few sentences here on how an easily reproducible article could help with all this.}
 
@@
 \label{sec:args:duplication}
-\xxx{We shouldn't have to ever reinvent the wheel. Astronomy should be collaborative. Time saved on duplicated effort can be invested in moving the field forward rather than always playing catch-up.}
+\todo[rodluger]{We shouldn't have to ever reinvent the wheel.
+Astronomy should be collaborative.
+Time saved on duplicated effort can be invested in moving the field forward rather than always playing catch-up.}
 %
-\xxx{Perhaps some stats on CPU usage in the field, and how reproducibility can help?}
+\todo[adrn][dfm]{Perhaps some stats on CPU usage in the field, and how reproducibility can help?}
 %
-\xxx{Can also talk about open data here; e.g., telescope time is super competitive; we should make it easy for others to use our data, both raw and processed.}
+\todo[adrn][dfm]{Can also talk about open data here; e.g., telescope time is super competitive; we should make it easy for others to use our data, both raw and processed.}
 
@@
 \label{sec:args:dei}
-\xxx{Proprietary legacy code is antithetical to DEI.
+\todo[rodluger][adrn]{Proprietary legacy code is antithetical to DEI.
 ``Source code available upon request'' is antithetical to DEI.
@@
 \label{sec:intro:curr}
-\xxx{Discuss code links in \citet{Luger2019,Luger2021a,Luger2021b}, and how they have caught on, e.g., \citet{Paillas2022}.} 
+\todo[rodluger]{Discuss code links in \citet{Luger2019,Luger2021a,Luger2021b}, and how they have caught on, e.g., \citet{Paillas2022}.} 
 %
-\xxx{Give a detailed overview of reproducibility in astronomy; \href{https://maneage.org/pdf/slides-intro.pdf}{this page} has some nice resources.
+\todo[rodluger][adrn][dfm]{Give a detailed overview of reproducibility in astronomy; \href{https://maneage.org/pdf/slides-intro.pdf}{this page} has some nice resources.
 Look at reviews by Harlan Krumholz in medicine.
@@
     \begin{centering}
-        \includegraphics[width=0.8\linewidth]{figures/tree.pdf}
+        \includegraphics[width=0.5\linewidth]{figures/tree.pdf}
         \caption{
@@
 %
-\xxx{More details here.}
+\todo[rodluger]{More details here.}
 
@@
 \label{sec:how-it-works}
-\xxx{Discuss how things are actually implemented.
+\todo[rodluger]{Discuss how things are actually implemented.
 Talk about the dependence on \snakemake \citep{Molder2021} and \tectonic.
@@
 Figure~\ref{fig:two_moons} is an example of a figure depending on an intermediate result that is cached on Zenodo Sandbox.
-\xxx{More details.}
+\todo[rodluger]{More details.}
 
-\xxx{Discuss Table~\ref{tab:variable} and variable output.}
+\todo[rodluger]{Discuss Table~\ref{tab:variable} and variable output.}
 Variable output can also occur inline. For instance, the following sentence is programmatically generated from the same script: 
@@
 
-\xxx{Discuss Figure~\ref{fig:dag} and this paper as a whole as a meta-example.}
+\todo[rodluger]{Discuss Figure~\ref{fig:dag} and this paper as a whole as a meta-example.}
 
-\xxx{Finally, cite a bunch of papers here that already use showyourwork and showcase its various features.}
+\todo[rodluger]{Finally, cite a bunch of papers here that already use showyourwork and showcase its various features.}
 
@@
 \label{sec:future}
-\xxx{This is a work in progress.
+\todo[rodluger][dfm][mathren][milescranmer]{This is a work in progress.
 Currently focused primarily on short-term reproducibility; discuss the various issues that arise from relying on \GitHub, \conda, \pip, etc.
@@
 \label{sec:conclusion}
-\xxx{Stuff here. showyourwork is a community project -- please contribute!}
+\todo[rodluger][dfm][adrn][milescranmer][jfcrenshaw][mathren][katiebreivik][tomwagg]{Stuff here. showyourwork is a community project -- please contribute!}
 
@@
             and an intermediate dataset that was automatically cached on \Zenodo.
-            \xxx{@jfcrenshaw: is it ok for us to reproduce this figure of yours?}
         }
@@
     \end{center}
-    \caption{The functional forms of various commonly used Gaussian process kernels; reproduced from Table~1 in \citet{Aigrain2022}.
+        \caption{The functional forms of various commonly used Gaussian process kernels; based on Table~1 in \citet{Aigrain2022}.
         The contents of this table are programmatically generated; the kernels are defined as \sympy expressions and rendered into \TeX form in the script \repoargfile{src/scripts/kernels.py}.
         The autogenerated \GitHub icon in the margin links to the rule in the \repoargfile{Snakefile} that runs that script.
-    \xxx{@dfm: is it ok for us to reproduce this table of yours?}}
+    }
     \label{tab:variable}
@@
 The \repoargfile{src/static} directory is reserved for figures that are not programmatically generated and simply get copied over to the output directory at compile time.
-            \xxx{TODO: Regenerate me!}
         }

### 2022-10-21 src/scripts/kernels.py

@@ -36,4 +36,4 @@ params = {eval(key): value for key, value in params.items()}
 with open(paths.output / "kernel_value.tex", "w") as f:
     value = kernels[kernel].subs(params).evalf()
     params = ",\,".join([f"{key} = {value:.2f}" for key, value in params.items()])
-    f.write(rf"The value of the {kernel} kernel for ${params}$ is ${value:.5f}$.")
+    f.write(rf"the value of the {kernel} kernel for ${params}$ is ${value:.5f}$.")
